---
title: "Jet Lag quick analysis"
output:
  pdf_document: default
  html_document:
    df_print: paged
  html_notebook: default
---

#**================================================================**
#** Libraries and Environment Setup                  **
#**================================================================**
```{r}
#** Load necessary libraries *
# Using pacman to install and load packages in one step
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  # Original Libraries
  dplyr,          # For data manipulation
  tidyr,          # For data tidying
  openxlsx,       # For reading/writing Excel files
  lubridate,      # For easier date-time manipulation
  data.table,     # For efficient data handling, especially rleid
  pracma,         # For findpeaks
  GLMMcosinor,    # For generalized linear mixed cosinor models
  circacompare,   # For comparing circadian rhythms
  tidyverse,      # A collection of R packages for data science
  brms,           # For Bayesian regression models using Stan
  rstanarm,       # For Bayesian models via RStan
  paletteer,      # Provides a collection of color palettes
  ggcorrplot,     # For visualizing correlation matrices
  ggpubr,         # For publication-ready plots
  corrr,          # For exploring correlations
  qgraph,         # For network analysis and visualization
  combinat,       # For combinatorics
  zoo,            # For ordered time series data
  caret,          # For classification and regression training
  janitor,        # For simple data cleaning
  pwr,            # For power analysis
  lmPerm,         # For permutation tests for linear models
  mgcv,            # For permutation tests for GAM
  pwr,
  rstatix,
  hms,
  fs,
  car
  
)

#** --- Set up a valid path --- *
# Define base paths for both possible directories
base_paths <- c(
  "E:/OneDrive/TUNCOM/TUNCRG/06. Phase 2 Data/Aging",
  "C:/Users/samue/OneDrive/TUNCOM/TUNCRG/06. Phase 2 Data/Aging"
)

# Find the first existing directory
valid_path <- first(base_paths[dir.exists(base_paths)])

if (is.na(valid_path)) {
  stop("Neither of the specified base directories exists. Please check the paths.")
}

#** --- Define objects to keep --- *
# This list helps in managing the global environment
CoreDatasets <- c(
"CorsanoAnalysismulti", "CorsanoAnalysissingle", "CorsanoAnalysisSleepexpand", "SleepAnalysis", "StatS", "CoreDatasets", "subjects", "SplitModel2", "Statistics", "biomarkers", "SleepStat", "Analysis", "CorsanoAnalysissplit", "valid_path", "processed_subjects", "Stat", "processed_subjects1", "processed_subjects2", "processed_subjects3", "CorsanoAnalysisAll", "Shiftwork", "Shiftwork2", "ShiftStat", "Sleepwork", "CorsanoAnalysisSleepmulti", "CorsanoAnalysisSleepsingle", "CorsanoAnalysisWave", "PhaseDiff", "SLEEP", "CorsanoShiftWave", "Variability", "Stability", "SJL", "StatSS", "SLEEP1", "AmpMesAge", "AmpMesGen", "BioBmiStats", "DeviationsS", "SJLDeviations", "SJLBIO", "jsl_summary", "Jetlag", "biolist", "PhysCog", "Aging", "AgingA", "SJL2", "SJLBio"
)


# Biolist
biolist <- c("HR", "Steps", "Energy", "Breath", "HRV", "RR", "Cortisol", "Stress", "SBT", "CBT")

# Clean up
rm(list = setdiff(ls(), CoreDatasets))
```



# Clean StatSS for use in analysis
```{r}
SJL <- StatSS %>%
  clean_names()
```


#**================================================================**
#** All biometric Amplitude and mesor analysis vs age and gender   **
#**================================================================**
```{r}

# --- INITIALIZE DATAFRAMES TO STORE RESULTS ---

# For Age-based analysis of Amplitude and Mesor correlations
AmpMesAge <- data.frame(
  Biometric = character(),
  week = character(),
  age_group = character(),
  amp_corr_estimate = numeric(),
  amp_CI95 = character(),
  amp_pvalue = numeric(),
  amp_power = numeric(),
  mesor_corr_estimate = numeric(),
  mesor_CI95 = character(),
  mesor_pvalue = numeric(),
  mesor_power = numeric(),
  stringsAsFactors = FALSE
)

# For Gender-based analysis of Amplitude and Mesor differences
AmpMesGen <- data.frame(
  Biometric = character(),
  week = character(),
  Famplitude_mean = numeric(),
  Mamplitude_mean = numeric(),
  amp_CI95_diff = character(),
  amp_pvalue = numeric(),
  amp_power = numeric(),
  Fmesor_mean = numeric(),
  Mmesor_mean = numeric(),
  mesor_CI95_diff = character(),
  mesor_pvalue = numeric(),
  mesor_power = numeric(),
  stringsAsFactors = FALSE
)


#' Perform Analysis and capture statistical results into dataframes
#'
#' @param main_data The main dataframe (e.g., SJL).
#' @param period A string specifying the period to analyze: "Weekend", "Weekday", or "Both".
#' @param biometric A string specifying the biometric to analyze (e.g., "CBT", "HR").
analyze_bio_data <- function(main_data, period, biometric) {

  cat(paste("\n\n======================================================\n"))
  cat(paste("   PROCESSING:", biometric, "-", period, "\n"))
  cat(paste("======================================================\n\n"))

  # --- Filter Data ---
  SJLFiltered <- main_data %>%
    filter(!is.na(gender),
           bio == biometric,
           week == period)

  if (nrow(SJLFiltered) < 2) {
    cat(paste("Skipping: Not enough data for", biometric, "-", period, "\n"))
    return(invisible(NULL))
  }

  # --- Visualizations (Distribution and Box Plots) ---
  # These plots are kept for visual inspection during the run.
  # ... (visualization code remains largely the same) ...
  
  # --- Gender Differences in AMPLITUDE & MESOR ---
  female_amplitude <- SJLFiltered %>% filter(gender == "female") %>% pull(amplitude)
  male_amplitude <- SJLFiltered %>% filter(gender == "male") %>% pull(amplitude)
  female_mesor <- SJLFiltered %>% filter(gender == "female") %>% pull(mesor)
  male_mesor <- SJLFiltered %>% filter(gender == "male") %>% pull(mesor)

  # Initialize variables to NA
  f_amp_mean <- NA; m_amp_mean <- NA; amp_ci_diff <- NA; amp_p <- NA; amp_pow <- NA
  f_mes_mean <- NA; m_mes_mean <- NA; mes_ci_diff <- NA; mes_p <- NA; mes_pow <- NA

  # Amplitude T-Test
  if (length(female_amplitude) > 1 && length(male_amplitude) > 1) {
    t_test_amp <- t.test(female_amplitude, male_amplitude)
    f_amp_mean <- t_test_amp$estimate[1]
    m_amp_mean <- t_test_amp$estimate[2]
    amp_ci_diff <- paste(round(t_test_amp$conf.int, 3), collapse = " to ")
    amp_p <- t_test_amp$p.value
    
    # Power for amplitude
    cohen_d_amp <- abs(f_amp_mean - m_amp_mean) / sd(c(female_amplitude, male_amplitude))
    if(!is.na(cohen_d_amp) && cohen_d_amp > 0) {
        power_amp_res <- pwr.t2n.test(n1 = length(female_amplitude), n2 = length(male_amplitude), d = cohen_d_amp, sig.level = 0.05)
        amp_pow <- power_amp_res$power
    }
  }

  # Mesor T-Test
  if (length(female_mesor) > 1 && length(male_mesor) > 1) {
    t_test_mesor <- t.test(female_mesor, male_mesor)
    f_mes_mean <- t_test_mesor$estimate[1]
    m_mes_mean <- t_test_mesor$estimate[2]
    mes_ci_diff <- paste(round(t_test_mesor$conf.int, 3), collapse = " to ")
    mes_p <- t_test_mesor$p.value

    # Power for mesor
    cohen_d_mesor <- abs(f_mes_mean - m_mes_mean) / sd(c(female_mesor, male_mesor))
     if(!is.na(cohen_d_mesor) && cohen_d_mesor > 0) {
        power_mesor_res <- pwr.t2n.test(n1 = length(female_mesor), n2 = length(male_mesor), d = cohen_d_mesor, sig.level = 0.05)
        mes_pow <- power_mesor_res$power
    }
  }

  # Add results to AmpMesGen dataframe
  AmpMesGen <<- AmpMesGen %>%
    add_row(
      Biometric = biometric, week = period,
      Famplitude_mean = f_amp_mean, Mamplitude_mean = m_amp_mean,
      amp_CI95_diff = amp_ci_diff, amp_pvalue = amp_p, amp_power = amp_pow,
      Fmesor_mean = f_mes_mean, Mmesor_mean = m_mes_mean,
      mesor_CI95_diff = mes_ci_diff, mesor_pvalue = mes_p, mesor_power = mes_pow
    )

  # --- Amplitude & Mesor vs. Age Analysis by Age Group ---
  SJLFiltered <- SJLFiltered %>%
    mutate(age_group = cut(age,
                           breaks = c(19, 40, 70, Inf),
                           labels = c("20-40", "41-70", "71+"),
                           include.lowest = TRUE))
    
  age_groups <- unique(SJLFiltered$age_group)
  age_groups <- age_groups[!is.na(age_groups)]

  for(ag in age_groups) {
    group_data <- SJLFiltered %>% filter(age_group == ag)

    amp_corr <- NA; amp_ci <- NA; amp_p <- NA; amp_pow <- NA
    mes_corr <- NA; mes_ci <- NA; mes_p <- NA; mes_pow <- NA
    
    # Amplitude vs Age Correlation
    if (nrow(group_data) > 2) {
      cor_test_amp <- cor.test(group_data$age, group_data$amplitude, method = "pearson")
      amp_corr <- cor_test_amp$estimate
      amp_ci <- paste(round(cor_test_amp$conf.int, 3), collapse = " to ")
      amp_p <- cor_test_amp$p.value
      amp_pow_res <- pwr.r.test(n = nrow(group_data), r = amp_corr, sig.level = 0.05)
      amp_pow <- amp_pow_res$power

      # NEW: Visualization of Amplitude vs. Age
      plot_amp_age <- ggplot(group_data, aes(x = age, y = amplitude)) +
        geom_point(alpha = 0.7, color = "blue") +
        geom_smooth(method = "lm", se = FALSE, color = "red") +
        labs(
          title = paste(biometric, "Amplitude vs. Age -", period),
          subtitle = paste("Age Group:", ag),
          x = "Age",
          y = "Amplitude"
        ) +
        theme_minimal()
      print(plot_amp_age)
    }
    
    # Mesor vs Age Correlation
    if (nrow(group_data) > 2) {
      cor_test_mes <- cor.test(group_data$age, group_data$mesor, method = "pearson")
      mes_corr <- cor_test_mes$estimate
      mes_ci <- paste(round(cor_test_mes$conf.int, 3), collapse = " to ")
      mes_p <- cor_test_mes$p.value
      mes_pow_res <- pwr.r.test(n = nrow(group_data), r = mes_corr, sig.level = 0.05)
      mes_pow <- mes_pow_res$power
      
      # NEW: Visualization of Mesor vs. Age
      plot_mes_age <- ggplot(group_data, aes(x = age, y = mesor)) +
        geom_point(alpha = 0.7, color = "purple") +
        geom_smooth(method = "lm", se = FALSE, color = "orange") +
        labs(
          title = paste(biometric, "Mesor vs. Age -", period),
          subtitle = paste("Age Group:", ag),
          x = "Age",
          y = "Mesor"
        ) +
        theme_minimal()
      print(plot_mes_age)
    }

    # Add results to AmpMesAge dataframe
    AmpMesAge <<- AmpMesAge %>%
      add_row(
        Biometric = biometric, week = period, age_group = as.character(ag),
        amp_corr_estimate = amp_corr, amp_CI95 = amp_ci, amp_pvalue = amp_p, amp_power = amp_pow,
        mesor_corr_estimate = mes_corr, mesor_CI95 = mes_ci, mesor_pvalue = mes_p, mesor_power = mes_pow
      )
  }
}

# --- RUN THE ANALYSIS FOR EACH BIOMETRIC AND PERIOD ---
unique_bios <- unique(SJL$bio)
unique_bios <- unique_bios[!is.na(unique_bios)]
periods <- c("Weekend", "Weekday", "Both")

for (current_bio in unique_bios) {
  for (current_period in periods) {
    # Use tryCatch to prevent one error from stopping the entire loop
    try(analyze_bio_data(SJL, current_period, current_bio), silent = TRUE)
  }
}

# --- DISPLAY FINAL RESULTS ---
cat("\n\n======================================================\n")
cat("           RESULTS SUMMARY - GENDER ANALYSIS\n")
cat("======================================================\n\n")
print(head(AmpMesGen))

cat("\n\n======================================================\n")
cat("            RESULTS SUMMARY - AGE ANALYSIS\n")
cat("======================================================\n\n")
print(head(AmpMesAge))

# --- Export the Final Data ---
export_path <- file.path(valid_path, "Stats", "AmpMesAge.xlsx")
write.xlsx(AmpMesAge, export_path, rowNames = FALSE, firstRow = TRUE)
cat("Analysis complete. Data exported to:", export_path, "\n")
export_path <- file.path(valid_path, "Stats", "AmpMesGender.xlsx")
write.xlsx(AmpMesGen, export_path, rowNames = FALSE, firstRow = TRUE)
cat("Analysis complete. Data exported to:", export_path, "\n")

# --- NEW ANALYSIS: Overall Age vs. Amplitude for "Both" Period ---
cat("\n\n======================================================\n")
cat("   PLOTTING: Overall Age vs. Amplitude for 'Both' Period\n")
cat("======================================================\n\n")

# 1. Filter the main dataframe for the "Both" period
SJLFilteredBoth <- SJL %>%
  filter(week == "Both", !is.na(age), !is.na(amplitude))

# 2. Get the unique biometrics to loop through from this filtered data
unique_bios_both <- unique(SJLFilteredBoth$bio)
unique_bios_both <- unique_bios_both[!is.na(unique_bios_both)]

# 3. Loop through each biometric to create a plot
for (current_bio in unique_bios_both) {
  
  # a. Filter for the current biometric
  bio_data <- SJLFilteredBoth %>%
    filter(bio == current_bio)
  
  # b. Check if there's enough data to plot
  if (nrow(bio_data) > 2) {
    cat(paste("--- Generating plot for:", current_bio, "---\n"))
    
    # c. Create the scatter plot
    plot_age_amp <- ggplot(bio_data, aes(x = age, y = amplitude)) +
      geom_point(alpha = 0.7, color = "darkcyan") +
      geom_smooth(method = "lm", se = FALSE, color = "orangered") +
      labs(
        title = paste("Amplitude vs. Age for", current_bio),
        subtitle = "Period: Both",
        x = "Age",
        y = "Amplitude"
      ) +
      theme_minimal()
      
    # d. Print the plot to the R console/plot pane
    print(plot_age_amp)
    
  } else {
    cat(paste("--- Skipping plot for:", current_bio, "(not enough data) ---\n"))
  }
}


# Clean up
rm(list = setdiff(ls(), CoreDatasets))


```



#**================================================================**
#** All biometric Amplitude and mesor analysis vs BMI              **
#**================================================================**
```{r}
# --- INITIALIZE DATAFRAME TO STORE RESULTS ---
# This dataframe will collect all the statistical results from the BMI analysis.
BioBmiStats <- data.frame(
  Biometric = character(),
  Period = character(),
  Metric = character(),
  Correlation_Estimate = numeric(),
  CI_95 = character(),
  P_Value = numeric(),
  Power = numeric(),
  SampleSize = integer(),
  stringsAsFactors = FALSE
)


#' Perform Analysis for a specific biometric, period, and metric against BMI
#'
#' @param main_data The main dataframe (e.g., SJL).
#' @param period A string specifying the period to analyze: "Weekend", "Weekday", or "Both".
#' @param biometric A string specifying the biometric to analyze (e.g., "CBT", "HR").
#' @param metric_to_compare A string for the column to correlate with BMI (e.g., "amplitude", "max").
analyze_bio_data <- function(main_data, period, biometric, metric_to_compare) {

  # Capitalize the first letter of the metric for clean labeling
  metric_label <- paste0(toupper(substring(metric_to_compare, 1, 1)), substring(metric_to_compare, 2))

  cat(paste("\n\n======================================================\n"))
  cat(paste("   ANALYZING:", biometric, "-", period, " (Metric:", metric_label, "vs. BMI)\n"))
  cat(paste("======================================================\n\n"))

  # --- Filter Data ---
  # Filter the data based on the specified biometric and period.
  SJLFiltered <- main_data %>%
    filter(!is.na(gender),
           bio == biometric,
           week == period,
           !is.na(.data[[metric_to_compare]]), # Ensure the metric to compare is not NA
           !is.na(bmi) # Ensure bmi is not NA
           )

  # Check if there is enough data to proceed
  if (nrow(SJLFiltered) < 3) {
    cat(paste("Skipping: Not enough data for", biometric, "-", period, "(Metric:", metric_label, ")\n"))
    return(invisible(NULL)) # Exit the function
  }

  # --- Metric vs. BMI Correlation Analysis ---
  
  # Initialize variables to hold results
  corr_est <- NA; ci_95 <- NA; p_val <- NA; power_val <- NA
  
  # Use tryCatch to handle potential errors during correlation testing
  tryCatch({
    cor_test_result <- cor.test(SJLFiltered$bmi, SJLFiltered[[metric_to_compare]], method = "pearson")
    
    # Extract results from the correlation test
    corr_est <- cor_test_result$estimate
    ci_95 <- paste(round(cor_test_result$conf.int, 3), collapse = " to ")
    p_val <- cor_test_result$p.value
    
    # Power Analysis
    if (!is.na(corr_est)) {
      power_res <- pwr.r.test(n = nrow(SJLFiltered), r = corr_est, sig.level = 0.05)
      power_val <- power_res$power
    }
  }, error = function(e) {
    cat(paste("An error occurred during correlation test for", biometric, "-", period, ":", e$message, "\n"))
  })

  # --- Add Results to the Main DataFrame ---
  # Use the <<- operator to modify the global BioBmiStats dataframe from within the function
  BioBmiStats <<- BioBmiStats %>%
    add_row(
      Biometric = biometric,
      Period = period,
      Metric = metric_to_compare,
      Correlation_Estimate = corr_est,
      CI_95 = ci_95,
      P_Value = p_val,
      Power = power_val,
      SampleSize = nrow(SJLFiltered)
    )

  # --- Visualization of Metric vs. BMI ---
  # This part remains to provide a visual check of the relationship.
  # ... (visualization code remains the same) ...
  Q1_metric <- quantile(SJLFiltered[[metric_to_compare]], 0.25, na.rm = TRUE)
  Q3_metric <- quantile(SJLFiltered[[metric_to_compare]], 0.75, na.rm = TRUE)
  IQR_metric <- Q3_metric - Q1_metric
  lower_bound_metric <- Q1_metric - 1.5 * IQR_metric
  upper_bound_metric <- Q3_metric + 1.5 * IQR_metric

  scatter_plot_bmi <- ggplot(SJLFiltered, aes(x = bmi, y = .data[[metric_to_compare]])) +
    geom_point(color = "blue") +
    geom_smooth(method = "lm", se = FALSE, color = "red") +
    labs(title = paste(biometric, metric_label, "vs. BMI -", period),
         x = "BMI",
         y = paste(biometric, metric_label)) +
    theme_minimal() +
    coord_cartesian(ylim = c(lower_bound_metric, upper_bound_metric))
  
  print(scatter_plot_bmi)
}

# --- RUN THE ANALYSIS FOR EACH BIOMETRIC AND PERIOD ---

# Define the specific biometrics and metrics to analyze
biometrics_to_analyze <- unique(na.omit(SJL$bio))
metrics_to_analyze <- c("amplitude", "max", "min", "mesor")
periods <- c("Weekend", "Weekday", "Both")

# Loop through each biometric, then each period, then each metric, and run the analysis
for (current_bio in biometrics_to_analyze) {
  for (current_period in periods) {
    for (current_metric in metrics_to_analyze) {
      # Use try() to ensure one error doesn't stop the entire loop
      try(analyze_bio_data(SJL, current_period, current_bio, current_metric))
    }
  }
}

# --- DISPLAY FINAL RESULTS DATAFRAME ---
cat("\n\n======================================================\n")
cat("          RESULTS SUMMARY - BIOMETRIC vs. BMI\n")
cat("======================================================\n\n")
print(head(BioBmiStats))


# --- Export the Final Data ---
export_path <- file.path(valid_path, "Stats", "BMI.xlsx")
write.xlsx(BioBmiStats, export_path, rowNames = FALSE, firstRow = TRUE)
cat("Analysis complete. Data exported to:", export_path, "\n")


# Clean up
rm(list = setdiff(ls(), CoreDatasets))
```



#**================================================================**
#** Correlations of amplitude between biometrics between age groups**
#**================================================================**
```{r}
# --- Optimized Correlation Analysis of Biometric Amplitudes by Age Group ---

# 1. Prepare the data in a single, chained operation
amplitude_data <- SJL %>%
  filter(!is.na(week), week == "Weekday") %>%
  mutate(age_group = cut(age,
                         breaks = c(19, 40, 70, Inf),
                         labels = c("20-40", "41-70", "71+"),
                         include.lowest = TRUE)) %>%
  # Summarize multiple readings by taking the average amplitude
  group_by(patient, bio, age_group) %>%
  summarise(amplitude = mean(amplitude, na.rm = TRUE), .groups = 'drop') %>%
  na.omit()

# 2. Get unique age groups to iterate over
age_groups <- unique(amplitude_data$age_group)

# 3. Initialize lists to store results for each group
correlation_list <- list()
matrices_to_export <- list() 

# Helper function to calculate pairwise sample sizes (n)
pairwise_n <- function(df) {
  as.matrix(t(!is.na(df))) %*% as.matrix(!is.na(df))
}

# Determine a master order for biometrics to ensure consistent axes
all_data_wide <- amplitude_data %>%
  tidyr::pivot_wider(names_from = bio, values_from = amplitude) %>%
  select(-patient, -age_group)
master_cor_matrix <- cor(all_data_wide, use = "pairwise.complete.obs")
master_order <- colnames(master_cor_matrix)[hclust(dist(master_cor_matrix))$order]

# Define the output directory for exports at the beginning
# This assumes 'valid_path' is defined earlier in your script. If not, set it here.
# For example: valid_path <- getwd() 
output_dir <- file.path(valid_path, "Stats")
if (!dir.exists(output_dir)) {
  dir.create(output_dir, recursive = TRUE)
  cat("Created directory:", output_dir, "\n")
}


# 4. Use a single loop to perform analysis, visualization, and data extraction
for (group in age_groups) {
  
  # a. Filter data for the current age group and pivot to wide format
  group_data_wide <- amplitude_data %>%
    filter(age_group == group) %>%
    tidyr::pivot_wider(names_from = bio, values_from = amplitude) %>%
    select(-patient, -age_group) 

  # b. Check if there's enough data for correlation
  if (ncol(group_data_wide) > 1) {
    
    # c. Calculate correlation and sample size matrices ONCE
    cor_matrix <- cor(group_data_wide, use = "pairwise.complete.obs")
    n_matrix <- pairwise_n(group_data_wide)

    # Store the formatted matrix for Excel export
    matrices_to_export[[as.character(group)]] <- as.data.frame(cor_matrix) %>%
      rownames_to_column("Biometric")

    # d. Print the correlation matrix
    cat("\n--- Correlation Matrix for Age Group:", as.character(group), "---\n")
    print(cor_matrix)

    # e. Visualize the correlation matrix
    cat("\n--- Visualizing Correlation for Age Group:", as.character(group), "---\n")
    
    # Reorder the current group's matrix based on the master order
    plot_order <- master_order[master_order %in% colnames(cor_matrix)]
    cor_matrix_ordered <- cor_matrix[plot_order, plot_order]
    
    corr_plot <- ggcorrplot(cor_matrix_ordered,
                            hc.order = FALSE,
                            type = "lower",
                            lab = TRUE,
                            lab_size = 3,
                            title = paste("Correlation of Biometric Amplitudes -", group, "Group"))
    print(corr_plot)
    
    # Export the plot to a PNG file
    plot_filename <- paste0("Correlation Matrix ", gsub("[^A-Za-z0-9]+", " ", as.character(group)), ".png")
    plot_export_path <- file.path(output_dir, plot_filename)
    ggsave(plot_export_path, plot = corr_plot, width = 8, height = 7, dpi = 300)
    cat("   > Plot saved to:", plot_export_path, "\n")


    # f. Tidy the correlation and n matrices and join them
    cor_tidy <- as.data.frame(cor_matrix) %>%
      rownames_to_column("bio_x") %>%
      pivot_longer(cols = -bio_x, names_to = "bio_y", values_to = "correlation")

    n_tidy <- as.data.frame(n_matrix) %>%
      rownames_to_column("bio_x") %>%
      pivot_longer(cols = -bio_x, names_to = "bio_y", values_to = "n")

    # Join results and store in the list
    correlation_list[[as.character(group)]] <- inner_join(cor_tidy, n_tidy, by = c("bio_x", "bio_y")) %>%
      filter(bio_x < bio_y) %>% 
      mutate(age_group = group)
    
  } else {
    cat("\n--- Not enough data for correlation matrix in Age Group:", as.character(group), "---\n")
  }
}

# 5. Combine the list of results into a single data frame AFTER the loop
all_correlations <- bind_rows(correlation_list)

# 6. Print the final, compiled list of all correlations
cat("\n\n--- Compiled List of All Correlation Values ---\n")
print(all_correlations)


# --- Fisher Z-Test for Comparing Correlation Coefficients ---
compare_correlations_z_test <- function(r1, n1, r2, n2) {
  z1 <- 0.5 * log((1 + r1) / (1 - r1))
  z2 <- 0.5 * log((1 + r2) / (1 - r2))
  se_diff <- sqrt(1 / (n1 - 3) + 1 / (n2 - 3))
  z_stat <- (z1 - z2) / se_diff
  p_value <- 2 * (1 - pnorm(abs(z_stat)))
  return(list(z_statistic = z_stat, p_value = p_value))
}

# --- Perform Significance Testing Between All Age Group Pairs ---
if (length(age_groups) > 1) {

  age_group_pairs <- combn(as.character(age_groups), 2, simplify = FALSE)
  comparison_results_list <- list()
  
  for (pair in age_group_pairs) {
    group1_label <- pair[1]
    group2_label <- pair[2]
    
    group1_data <- all_correlations %>% filter(age_group == group1_label)
    group2_data <- all_correlations %>% filter(age_group == group2_label)
    
    comparison_df <- inner_join(group1_data, group2_data, by = c("bio_x", "bio_y"), suffix = c("_g1", "_g2"))
    
    if (nrow(comparison_df) > 0) {
      test_results <- comparison_df %>%
        rowwise() %>%
        mutate(test_result = list(compare_correlations_z_test(correlation_g1, n_g1, correlation_g2, n_g2))) %>%
        ungroup() %>%
        mutate(z_statistic = sapply(test_result, `[[`, "z_statistic"),
               p_value = sapply(test_result, `[[`, "p_value")) %>%
        select(-test_result)
        
      comparison_results_list[[paste(group1_label, "vs", group2_label)]] <- test_results
    }
  }

  final_comparison_results <- bind_rows(comparison_results_list) %>%
    mutate(significant = ifelse(p_value < 0.05, "Yes", "No")) %>%
    select(bio_x, bio_y, 
           age_group_g1, correlation_g1, n_g1,
           age_group_g2, correlation_g2, n_g2,
           z_statistic, p_value, significant)

  cat("\n\n--- Comparison of Correlations Between Age Groups (Fisher Z-Test) ---\n")
  print(final_comparison_results)
  
  significant_findings <- final_comparison_results %>% filter(significant == "Yes")
  if(nrow(significant_findings) > 0) {
    cat("\n\n--- Summary of Significant Differences ---\n")
    print(significant_findings)
  } else {
    cat("\n\n--- No significant differences in correlations were found between any age groups. ---\n")
  }

} else {
  cat("\n\n--- Not enough age groups to perform a comparison. ---\n")
  final_comparison_results <- data.frame() 
}

# --- NEW: Visualize Correlation Differences Across Age Groups ---
if (nrow(all_correlations) > 0) {
  cat("\n\n--- Visualizing Differences in Correlations by Age Group ---\n")
  
  # Create a combined label for faceting
  all_correlations <- all_correlations %>%
    mutate(biometric_pair = paste(bio_x, "-", bio_y))
    
  # Create the faceted bar plot
  comparison_plot <- ggplot(all_correlations, aes(x = age_group, y = correlation, fill = age_group)) +
    geom_bar(stat = "identity", position = "dodge") +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
    facet_wrap(~biometric_pair) +
    labs(
      title = "Comparison of Biometric Correlations Across Age Groups",
      x = "Age Group",
      y = "Correlation Coefficient"
    ) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(size = 8)) # Adjust text size for readability
          
  print(comparison_plot)
  
  # Export the comparison plot
  comparison_plot_path <- file.path(output_dir, "Correlation Comparison by Age Group.png")
  ggsave(comparison_plot_path, plot = comparison_plot, width = 12, height = 10, dpi = 300)
  cat("   > Comparison plot saved to:", comparison_plot_path, "\n")
}


# --- Export the Final Data to Excel ---
final_export_list <- c(
  list("Significance_Tests" = final_comparison_results), 
  matrices_to_export
)

excel_export_path <- file.path(output_dir, "Correlation Comparisons Age Groups.xlsx")
write.xlsx(final_export_list, excel_export_path, rowNames = FALSE, firstRow = TRUE, overwrite = TRUE)
cat("\nAnalysis complete. Data including significance tests and raw correlation matrices exported to:", excel_export_path, "\n")


# Clean up
rm(list = setdiff(ls(), CoreDatasets))
```




#**================================================================**
#** Analysis of Combined Phase Shifts and Deviations               **
#**================================================================**
```{r}
# --- Analysis of Phase Shifts (p_phase and t_phase) ---

# 1. Define helper functions for calculating cyclical differences and variance.

# Calculates the shortest difference between two points on a 24-hour cycle.
calculate_phase_difference <- function(phase1, phase2, cycle_length = 24) {
  diff <- abs(phase1 - phase2)
  pmin(diff, cycle_length - diff)
}

# Calculates circular variance for cyclical data.
circular_variance <- function(x, cycle_length = 24) {
  if (length(na.omit(x)) < 2) return(NA)
  x_rad <- (x / cycle_length) * 2 * pi
  # Calculate mean resultant vector length (R)
  R <- sqrt(sum(cos(x_rad))^2 + sum(sin(x_rad))^2) / length(x)
  1 - R # Return variance
}


# 2. Optimized Pipeline: Prepare data and calculate phase differences in one step.
# The resulting dataframe contains the per-patient, per-biometric phase shifts.
phase_differences <- SJL %>%
  # Filter out 'Both' week type and any rows with NA in 'week'
  filter(!is.na(week), week != "Both") %>%
  # Handle multiple readings by averaging the phase for each patient, week, and bio
  group_by(patient, week, bio) %>%
  summarise(
    p_phase = mean(p_phase, na.rm = TRUE),
    t_phase = mean(t_phase, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  # Pivot to a wide format to get Weekday and Weekend side-by-side
  pivot_wider(names_from = week, values_from = c(p_phase, t_phase)) %>%
  # This filter removes patients who do not have the core phase data for BOTH
  # Weekday and Weekend, which is the minimum requirement for this analysis.
  filter(!is.na(p_phase_Weekday) & !is.na(p_phase_Weekend) &
         !is.na(t_phase_Weekday) & !is.na(t_phase_Weekend)) %>%
  # Calculate cyclical differences and the total deviation magnitude
  mutate(
    p_phase_diff = calculate_phase_difference(p_phase_Weekday, p_phase_Weekend),
    t_phase_diff = calculate_phase_difference(t_phase_Weekday, t_phase_Weekend),
    magnitude_deviation = p_phase_diff + t_phase_diff
  )

# 3. Create the SJLBIO dataframe with per-patient, per-biometric shifts.
SJLBIO <- phase_differences %>%
  # Select the key columns for the final output
  select(patient, bio, p_phase_diff, t_phase_diff, magnitude_deviation)

cat("\n--- Per-Patient, Per-Biometric Phase Shift Summary (SJLBIO) ---\n")
print(SJLBIO)


# 4. Create the SJLDeviations dataframe with patient-level summary statistics (Phase Metrics).
SJLDeviations <- phase_differences %>%
  group_by(patient) %>%
  summarise(
    avg_total_deviation = mean(magnitude_deviation, na.rm = TRUE),
    sd_total_deviation = sd(magnitude_deviation, na.rm = TRUE),
    # Calculate circular variance and SD for the deviation magnitude
    circular_variance_deviation = circular_variance(magnitude_deviation),
    # Note: circular_sd requires variance to be < 1, will return NaN otherwise
    circular_sd_deviation = sqrt(-2 * log(1 - circular_variance_deviation)),
    mad_total_deviation = mad(magnitude_deviation, na.rm = TRUE),
    .groups = 'drop'
  )

cat("\n--- Patient-Level Deviation Summary (SJLDeviations) ---\n")
print(SJLDeviations)

# Both 'SJLBIO' and 'SJLDeviations' are now available in your environment.


# --- Correlation of Phase Deviation and Amplitude Deviation (OVERALL & BY BIOMETRIC) ---

# Create the directory for image exports if it doesn't exist
images_output_dir <- file.path(valid_path, "Stats/Images/PhaseDev")
if (!dir.exists(images_output_dir)) {
  dir.create(images_output_dir, recursive = TRUE)
  cat("Created directory for image exports:", images_output_dir, "\n")
}

# Initialize an empty list to store the results from all analyses
results_list <- list()

# --- Analysis 0: OVERALL Correlation ---
# 5. Calculate Overall Amplitude Deviation (Ampltide Metrics).
cat("\n\n--- Correlation for OVERALL: Phase Deviation vs. Overall Amplitude Deviation ---\n")

amplitude_diffs_overall <- SJL %>%
  filter(!is.na(week), week != "Both") %>%
  # Group by patient, week, AND bio to get mean amplitude for each
  group_by(patient, week, bio) %>%
  summarise(mean_amplitude = mean(amplitude, na.rm = TRUE), .groups = 'drop') %>%
  # Pivot to a wide format for comparison
  pivot_wider(names_from = week, values_from = mean_amplitude) %>%
  filter(!is.na(Weekday) & !is.na(Weekend)) %>%
  # Calculate the percentage difference for each biometric
  mutate(percent_diff = abs((Weekend - Weekday) / Weekday) * 100) %>%
  # NOW, group by patient to get a single average percentage difference across their biometrics
  group_by(patient) %>%
  summarise(overall_amplitude_percent_diff = mean(percent_diff, na.rm = TRUE), .groups = 'drop')


# 6. Combine all overall metrics into a single dataframe, SJL2.
# This dataframe contains all per-patient overall phase and amplitude deviation metrics.
SJL2 <- inner_join(SJLDeviations, amplitude_diffs_overall, by = "patient")

cat("\n--- Combined Patient-Level Deviation Data (SJL2) ---\n")
print(SJL2)


# Perform and store the overall correlations
if (nrow(SJL2) > 2) {
  # a. Average Deviation vs. Overall Amplitude
  correlation_test_avg_overall <- cor.test(
    SJL2$avg_total_deviation,
    SJL2$overall_amplitude_percent_diff,
    method = "spearman"
  )
  
  # --- Generate and export Quick Plot for Average Deviation ---
  plot_avg_overall <- ggplot(SJL2, aes(x = avg_total_deviation, y = overall_amplitude_percent_diff)) +
    geom_point(alpha = 0.7) + 
    geom_smooth(method = "lm", se = FALSE, color = "blue") +
    labs(title = "Overall Phase vs. Amplitude Deviation", 
         subtitle = "Average Phase Deviation", 
         x = "Average Phase Deviation (Hours)", 
         y = "Overall Amplitude Difference (%)") + 
    theme_minimal()
  print(plot_avg_overall)
  
  # Export the plot
  ggsave(
    file.path(images_output_dir, "Overall_Avg_Phase_vs_Amplitude_Deviation.png"),
    plot = plot_avg_overall, width = 8, height = 6, dpi = 300, bg = "white"
  )
  
  n_avg_overall <- nrow(SJL2)
  rho_avg_overall <- correlation_test_avg_overall$estimate
  power_avg_overall <- pwr.r.test(n = n_avg_overall, r = rho_avg_overall, sig.level = 0.05, alternative = "two.sided")$power
  results_list[[length(results_list) + 1]] <- data.frame(Biometric = "Overall", Analysis_Type = "Phase", p_value = correlation_test_avg_overall$p.value, sample_estimate_rho = rho_avg_overall, power = power_avg_overall)
  
  # b. MAD Deviation vs. Overall Amplitude
  correlation_test_mad_overall <- cor.test(
    SJL2$mad_total_deviation,
    SJL2$overall_amplitude_percent_diff,
    method = "spearman"
  )
  
  # --- Generate and export Quick Plot for MAD Deviation ---
  plot_mad_overall <- ggplot(SJL2, aes(x = mad_total_deviation, y = overall_amplitude_percent_diff)) +
    geom_point(alpha = 0.7) + 
    geom_smooth(method = "lm", se = FALSE, color = "red") +
    labs(title = "Overall Phase vs. Amplitude Deviation", 
         subtitle = "MAD of Phase Deviation", 
         x = "MAD of Phase Deviation (Hours)", 
         y = "Overall Amplitude Difference (%)") + 
    theme_minimal()
  print(plot_mad_overall)

  # Export the plot
  ggsave(
    file.path(images_output_dir, "Overall_MAD_Phase_vs_Amplitude_Deviation.png"),
    plot = plot_mad_overall, width = 8, height = 6, dpi = 300, bg = "white"
  )

  n_mad_overall <- nrow(SJL2)
  rho_mad_overall <- correlation_test_mad_overall$estimate
  power_mad_overall <- pwr.r.test(n = n_mad_overall, r = rho_mad_overall, sig.level = 0.05, alternative = "two.sided")$power
  results_list[[length(results_list) + 1]] <- data.frame(Biometric = "Overall", Analysis_Type = "MAD", p_value = correlation_test_mad_overall$p.value, sample_estimate_rho = rho_mad_overall, power = power_mad_overall)

} else {
  cat("Not enough combined data to perform overall correlation analysis.\n")
}


# --- Analysis 1-N: Per-Biometric Correlations ---
# This section calculates the amplitude difference for each biometric and then
# correlates it with the patient's overall phase deviation metrics (SJLDeviations).

amplitude_diffs_by_bio <- SJL %>%
  filter(!is.na(week), week != "Both") %>%
  group_by(patient, week, bio) %>%
  summarise(mean_amplitude = mean(amplitude, na.rm = TRUE), .groups = 'drop') %>%
  pivot_wider(names_from = week, values_from = mean_amplitude) %>%
  filter(!is.na(Weekday) & !is.na(Weekend)) %>%
  mutate(amplitude_percent_diff = abs((Weekend - Weekday) / Weekday) * 100) %>%
  select(patient, bio, amplitude_percent_diff)

combined_deviation_data_by_bio <- inner_join(SJLDeviations, amplitude_diffs_by_bio, by = "patient")
biometrics_to_analyze <- unique(combined_deviation_data_by_bio$bio)

for (current_bio in biometrics_to_analyze) {
  
  bio_data <- combined_deviation_data_by_bio %>% filter(bio == current_bio)
  
  # a. Average Phase Deviation vs. Amplitude Deviation
  cat(paste("\n--- Correlation for", current_bio, ": Average Phase Deviation vs. Amplitude Deviation ---\n"))
  
  if (nrow(bio_data) > 2) {
    correlation_test_avg <- cor.test(bio_data$avg_total_deviation, bio_data$amplitude_percent_diff, method = "spearman")
    print(correlation_test_avg)
    
    plot_avg <- ggplot(bio_data, aes(x = avg_total_deviation, y = amplitude_percent_diff)) +
      geom_point(alpha = 0.7) + geom_smooth(method = "lm", se = FALSE, color = "blue") +
      labs(title = paste("Phase vs. Amplitude Deviation for", current_bio), subtitle = "Average Phase Deviation", x = "Average Phase Deviation (Hours)", y = "Amplitude Difference (%)") + theme_minimal()
    print(plot_avg)
    
    # Export the plot
    ggsave(
      file.path(images_output_dir, paste0(current_bio, "_Avg_Phase_vs_Amplitude_Deviation.png")),
      plot = plot_avg, width = 8, height = 6, dpi = 300, bg = "white"
    )
    
    n_avg <- nrow(bio_data)
    rho_avg <- correlation_test_avg$estimate
    power_avg <- pwr.r.test(n = n_avg, r = rho_avg, sig.level = 0.05, alternative = "two.sided")$power
    results_list[[length(results_list) + 1]] <- data.frame(Biometric = current_bio, Analysis_Type = "Phase", p_value = correlation_test_avg$p.value, sample_estimate_rho = rho_avg, power = power_avg)
    
  } else {
    cat(paste("Not enough data for", current_bio, "to perform correlation for average deviation.\n"))
  }
  
  # b. MAD of Phase Deviation vs. Amplitude Deviation
  cat(paste("\n--- Correlation for", current_bio, ": MAD of Phase Deviation vs. Amplitude Deviation ---\n"))
  
  if (nrow(bio_data) > 2) {
    correlation_test_mad <- cor.test(bio_data$mad_total_deviation, bio_data$amplitude_percent_diff, method = "spearman")
    print(correlation_test_mad)
    
    plot_mad <- ggplot(bio_data, aes(x = mad_total_deviation, y = amplitude_percent_diff)) +
      geom_point(alpha = 0.7) + geom_smooth(method = "lm", se = FALSE, color = "red") +
      labs(title = paste("Phase vs. Amplitude Deviation for", current_bio), subtitle = "MAD of Phase Deviation", x = "MAD of Phase Deviation (Hours)", y = "Amplitude Difference (%)") + theme_minimal()
    print(plot_mad)
    
    # Export the plot
    ggsave(
      file.path(images_output_dir, paste0(current_bio, "_MAD_Phase_vs_Amplitude_Deviation.png")),
      plot = plot_mad, width = 8, height = 6, dpi = 300, bg = "white"
    )
    
    n_mad <- nrow(bio_data)
    rho_mad <- correlation_test_mad$estimate
    power_mad <- pwr.r.test(n = n_mad, r = rho_mad, sig.level = 0.05, alternative = "two.sided")$power
    results_list[[length(results_list) + 1]] <- data.frame(Biometric = current_bio, Analysis_Type = "MAD", p_value = correlation_test_mad$p.value, sample_estimate_rho = rho_mad, power = power_mad)
    
  } else {
    cat(paste("Not enough data for", current_bio, "to perform correlation for MAD deviation.\n"))
  }
}


# --- Compile and Export Statistical Analysis Results ---

# Create the DeviationsS dataframe from the list of results after all analyses.
if (length(results_list) > 0) {
  DeviationsS <- bind_rows(results_list)
  
  cat("\n\n--- Summary of Statistical Analyses (DeviationsS) ---\n")
  print(DeviationsS)
  
  export_path <- file.path(valid_path, "Stats", "Simple Deviations Overall and by Biometric.xlsx")
  write.xlsx(DeviationsS, export_path, rowNames = FALSE, firstRow = TRUE, overwrite = TRUE)
  cat("Analysis complete. Data exported to:", export_path, "\n")
  
  
export_path_bio <- file.path(valid_path, "Stats/SJLBIO.xlsx")
write.xlsx(SJLBIO, export_path_bio, rowNames = FALSE, firstRow = TRUE, overwrite = TRUE)
  
# Export the combined overall deviation data (SJL2) for external use, e.g., publication plots
export_path_sjl2 <- file.path(valid_path, "Stats/SJL2_Overall_Deviations.xlsx")
write.xlsx(SJL2, export_path_sjl2, rowNames = FALSE, firstRow = TRUE, overwrite = TRUE)
cat("Combined overall deviation data exported to:", export_path_sjl2, "\n")
  
} else {
  cat("\n\n--- Could not generate statistical summary as no correlation tests were successful. ---\n")
  DeviationsS <- data.frame() # Create an empty dataframe if no results
}




# Clean up
rm(list = setdiff(ls(), CoreDatasets))
```



#**================================================================**
#** 8. Overall Deviation Publication Plots                       **
#**================================================================**
```{r}
# This section generates high-quality scatter plots for the overall phase 
# vs. amplitude deviation correlations, relying on the 'SJL2' dataframe 
# created and persisted by the main analysis script (analysis.R).

# NOTE: SJL2 contains the columns 'avg_total_deviation', 'mad_total_deviation', 
# and 'overall_amplitude_percent_diff'.

# Filter SJL2 to ensure no NA values are used for plotting
plot_data_pub <- SJL2 %>%
  filter(!is.na(avg_total_deviation) & !is.na(overall_amplitude_percent_diff) &
         !is.na(mad_total_deviation))

if (nrow(plot_data_pub) == 0) {
  cat("ERROR: SJL2 is empty or contains no complete rows for deviation plotting.\n")
  # Exit script execution gracefully if no data is available
  # In R, this might be handled by conditional checks, or simply printing the error.
} else {

  # Create the directory for publication-quality exports
  output_dir <- file.path(valid_path, "Stats/PubPics")
  if (!dir.exists(output_dir)) {
    dir.create(output_dir, recursive = TRUE)
    cat("Created directory for publication exports:", output_dir, "\n")
  }

  # --- Plot 1: Average Phase Deviation vs. Overall Amplitude Deviation ---

  avg_dev_plot_pub <- ggplot(plot_data_pub, aes(x = avg_total_deviation, y = overall_amplitude_percent_diff)) +
    
    # Add scatter plot points (blue)
    geom_point(alpha = 0.7, color = "#1f77b4") + # A professional blue
    
    # Add GLM (linear fit) line
    geom_smooth(
      method = "lm",
      formula = y ~ x,
      color = "#d62728", # Red
      linetype = "solid",
      linewidth = 1.0,
      se = TRUE
    ) +
    
    # Apply Axis Limits (limit y axis to 150%)
    ylim(0, 150) +
    
    # Apply Labels (More descriptive titles for publication)
    labs(
      title = "Phase Deviation vs. Amplitude Deviation",
      
      x = "Absolute Phase Deviation (h)",
      y = "Overall Amplitude Difference (%)"
    ) +
    
    # Apply Clean Theme (using the user's preferred style)
    theme_minimal(base_size = 14) +
    theme(
      plot.title = element_text(face = "bold"),
      plot.subtitle = element_text(color = "black"),
      panel.grid.major = element_line(color = "black"), # Lighter gray grid lines
      panel.grid.minor = element_blank(),
      panel.grid.major.y = element_blank(),
      panel.background = element_rect(fill = "white", colour = NA), 
      plot.background = element_rect(fill = "white", colour = NA),
      axis.line = element_line(colour = "black") # Adding axis lines
    )

  # Display and Save Plot 1
  print(avg_dev_plot_pub)

  file_name_avg <- "Overall_Avg_Phase_vs_Amplitude_Deviation_Pub.png"
  output_path_avg <- file.path(output_dir, file_name_avg)
  ggsave(filename = output_path_avg, plot = avg_dev_plot_pub, width = 7.5, height = 5.6, units = "in", dpi = 300)
  cat(paste0("\nSaved Publication Plot (Avg Dev) to: ", output_path_avg, "\n"))


  # --- Plot 2: MAD Phase Deviation vs. Overall Amplitude Deviation ---

  mad_dev_plot_pub <- ggplot(plot_data_pub, aes(x = mad_total_deviation, y = overall_amplitude_percent_diff)) +
    
    # Add scatter plot points (darker blue)
    geom_point(alpha = 0.7, color = "#1f77b4") +
    
    # Add GLM (linear fit) line
    geom_smooth(
      method = "lm",
      formula = y ~ x,
      color = "#d62728", # Red
      linetype = "solid",
      linewidth = 1.0,
      se = TRUE
    ) +
    
    # Apply Axis Limits (limit y axis to 150%)
    ylim(0, 150) +
    
    # Apply Labels (More descriptive titles for publication)
    labs(
      title = "Mean Average Deviations of Phase Deviation vs. Amplitude Deviation",
      
      x = "Mean Phase Variability (h)",
      y = "Overall Amplitude Difference (%)"
    ) +
    
    # Apply Clean Theme (using the user's preferred style)
    theme_minimal(base_size = 14) +
    theme(
      plot.title = element_text(face = "bold"),
      plot.subtitle = element_text(color = "black"),
      panel.grid.major = element_line(color = "black"), # Lighter gray grid lines
      panel.grid.minor = element_blank(),
      panel.grid.major.y = element_blank(),
      panel.background = element_rect(fill = "white", colour = NA), 
      plot.background = element_rect(fill = "white", colour = NA),
      axis.line = element_line(colour = "black") # Adding axis lines
    )

  # Display and Save Plot 2
  print(mad_dev_plot_pub)

  file_name_mad <- "Overall_MAD_Phase_vs_Amplitude_Deviation_Pub.png"
  output_path_mad <- file.path(output_dir, file_name_mad)
  ggsave(filename = output_path_mad, plot = mad_dev_plot_pub, width = 7.5, height = 5.6, units = "in", dpi = 300)
  cat(paste0("\nSaved Publication Plot (MAD Dev) to: ", output_path_mad, "\n"))
  
} # End of check for plot_data_pub rows


# Clean up
rm(list = setdiff(ls(), CoreDatasets))
```




```{r}


lm_age_result <- lm(overall_amplitude_percent_diff ~ avg_total_deviation,
                    data = SJL2)

print(lm_age_result)

lm_age_result2 <- lm(overall_amplitude_percent_diff ~ mad_total_deviation,
                    data = SJL2)

print(lm_age_result2)
```















#**================================================================**
#** Analysis of social jetlag                                      **
#**================================================================**
```{r}
#==============================================================================
# Data Preparation
#==============================================================================
cat("--- Preparing data for Social Jetlag analysis ---\n")

# Create a separate dataframe for this analysis, filtering for only Weekday and Weekend
# Add age group stratification
SJLA <- SJL %>%
  filter(week %in% c("Weekday", "Weekend")) %>%
  mutate(age_group = cut(age,
                         breaks = c(19, 40, 70, Inf),
                         labels = c("20-40", "41-70", "71+"),
                         include.lowest = TRUE))

# Helper Function: Calculate Circular Difference (Absolute)
calculate_phase_difference <- function(phase1, phase2, cycle_length = 24) {
  diff <- abs(phase1 - phase2)
  pmin(diff, cycle_length - diff)
}


#==============================================================================
# Step 1 & 2: Calculate and Stratify Social Jetlag
#==============================================================================
cat("--- Step 1 & 2: Calculating and stratifying Social Jetlag ---\n")

sjl_summary <- SJLA %>%
  group_by(patient, week) %>%
  summarise(mean_mp = mean(p_phase, na.rm = TRUE), .groups = 'drop') %>%
  pivot_wider(names_from = week, values_from = mean_mp) %>%
  filter(!is.na(Weekday) & !is.na(Weekend)) %>%
  mutate(PhaseDev = calculate_phase_difference(Weekday, Weekend)) %>%
  mutate(sjl_severity = cut(PhaseDev,
                            breaks = c(-Inf, 1, 2, Inf),
                            labels = c("Mild (0-1h)", "Moderate (1-2h)", "Severe (2+h)"),
                            right = TRUE)) %>%
  select(patient, PhaseDev, sjl_severity)

# Add age group information to the main summary table
patient_info <- SJLA %>% distinct(patient, age_group)
sjl_summary <- inner_join(sjl_summary, patient_info, by = "patient")

cat("Social Jetlag summary created for", nrow(sjl_summary), "patients.\n")


#==============================================================================
# Step 3: Evaluate Weekday vs. Weekend Rhythm Changes
#==============================================================================
cat("\n--- Step 3: Calculating rhythm changes from Weekday to Weekend ---\n")

rhythm_changes_by_bio <- SJLA %>%
  group_by(patient, week, bio) %>%
  summarise(across(c(amplitude, mesor), ~mean(.x, na.rm = TRUE)), .groups = 'drop') %>%
  pivot_wider(names_from = week, values_from = c(amplitude, mesor)) %>%
  filter(if_all(starts_with(c("amplitude_", "mesor_")), ~!is.na(.))) %>%
  mutate(
    amplitude_directed_change = ((amplitude_Weekend - amplitude_Weekday) / amplitude_Weekday) * 100,
    amplitude_magnitude_change = abs(amplitude_directed_change)
  )

overall_amplitude_changes <- rhythm_changes_by_bio %>%
  group_by(patient) %>%
  summarise(
    overall_amplitude_directed_change = mean(amplitude_directed_change, na.rm = TRUE),
    overall_amplitude_magnitude_change = mean(amplitude_magnitude_change, na.rm = TRUE)
  )

#==============================================================================
# Main Analysis Loop
#==============================================================================
cat("\n--- Generating Analyses, Visualizations, and Statistical Summaries ---\n")

# Create the directory for image exports if it doesn't exist
# Note: Assumes a 'valid_path' variable is defined. If not, will save to the working directory.
if(!exists("valid_path")) valid_path <- getwd()
images_output_dir <- file.path(valid_path, "Stats", "Images", "Jetlag")
if (!dir.exists(images_output_dir)) {
  dir.create(images_output_dir, recursive = TRUE)
  cat("Created directory for image exports:", images_output_dir, "\n")
}


# Initialize an empty list to store the results dataframe from each group
results_list <- list()

# Define the groups to loop through: "Overall" and each age group
analysis_groups <- c("Overall", levels(SJLA$age_group))

for(group in analysis_groups) {
  
  cat(paste("\n\n======================================================================"))
  cat(paste("\n--- Running Analysis for Group:", group, "---"))
  cat(paste("\n======================================================================\n"))
  
  # Filter data for the current group
  if (group == "Overall") {
    current_sjl_summary <- sjl_summary
  } else {
    current_sjl_summary <- sjl_summary %>% filter(age_group == group)
  }
  
  # Check if there is enough data to proceed
  if(nrow(current_sjl_summary) < 3) {
    cat("Not enough data to run analysis for this group.\n")
    next # Skip to the next group
  }
  
  # Join data for the current group
  analysis_data <- inner_join(current_sjl_summary, overall_amplitude_changes, by = "patient")
  analysis_data_by_bio <- inner_join(current_sjl_summary, rhythm_changes_by_bio, by = "patient")

  # --- Overall Amplitude Change Analysis ---
  # A. Continuous Analysis (Correlation)
  correlation_overall <- cor.test(analysis_data$PhaseDev, analysis_data$overall_amplitude_magnitude_change, method = "spearman")
  power_corr_overall <- pwr.r.test(n = nrow(analysis_data), r = correlation_overall$estimate, sig.level = 0.05)$power
  results_list[[length(results_list) + 1]] <- data.frame(age_group = group, biometric = "Overall", test_type = "Correlation", p_value = correlation_overall$p.value, estimate = correlation_overall$estimate, power = power_corr_overall)

  plot_corr_overall <- ggplot(analysis_data, aes(x = PhaseDev, y = overall_amplitude_magnitude_change)) + geom_point(alpha = 0.6) + geom_smooth(method = "lm", se = FALSE, color = "blue") + labs(title = "Social Jetlag vs. Overall Amplitude Change", x = "SJL Magnitude (Hours)", y = "Overall Amplitude Change Mag. (%)") + theme_minimal()

  # B. Stratified Analysis (ANOVA)
  anova_overall <- aov(overall_amplitude_magnitude_change ~ sjl_severity, data = analysis_data)
  anova_summary <- summary(anova_overall)
  # Calculate effect size (f2) for power analysis
  ss_between <- anova_summary[[1]]["sjl_severity", "Sum Sq"]
  ss_within <- anova_summary[[1]]["Residuals", "Sum Sq"]
  f2 <- ss_between / ss_within
  power_anova_overall <- pwr.f2.test(u = anova_summary[[1]]["sjl_severity", "Df"], v = anova_summary[[1]]["Residuals", "Df"], f2 = f2, sig.level = 0.05)$power
  results_list[[length(results_list) + 1]] <- data.frame(age_group = group, biometric = "Overall", test_type = "ANOVA", p_value = anova_summary[[1]][1, "Pr(>F)"], estimate = anova_summary[[1]][1, "F value"], power = power_anova_overall)

  plot_stratified_overall <- ggplot(analysis_data, aes(x = sjl_severity, y = overall_amplitude_magnitude_change, fill = sjl_severity)) + geom_boxplot(alpha = 0.7) + labs(title = "Overall Amplitude Change by SJL Severity", x = "SJL Group", y = "Overall Amplitude Change Mag. (%)") + theme_minimal() + theme(legend.position = "none")

  # C. Combined Plot for Overall Analysis
  combined_overall_plot <- ggarrange(plot_corr_overall, plot_stratified_overall, ncol = 2, nrow = 1)
  overall_plot_annotated <- annotate_figure(combined_overall_plot, top = text_grob(paste("Overall Analysis for Group:", group), face = "bold", size = 16))
  print(overall_plot_annotated)
  
  # Export the combined overall plot
  plot_filename_overall <- paste0("Overall_Analysis_", gsub("[^A-Za-z0-9]+", "_", group), ".png")
  ggsave(
    file.path(images_output_dir, plot_filename_overall),
    plot = overall_plot_annotated,
    width = 12, height = 6, dpi = 300, bg = "white"
  )
  cat(" > Overall plot saved for group:", group, "\n")


  # --- Per-Biometric Analysis ---
  biometrics_to_analyze <- unique(analysis_data_by_bio$bio)
  for(current_bio in biometrics_to_analyze) {
    
    cat(paste("\n--- Analyzing Biometric:", current_bio, "for Group:", group, "---\n"))
    
    bio_data <- analysis_data_by_bio %>% filter(bio == current_bio)
    if(nrow(bio_data) < 3) {
      cat("Not enough data for analysis.\n")
      next
    }
    
    # --- Visualization for Per-Biometric ---
    # A. Continuous Plot
    plot_corr_bio <- ggplot(bio_data, aes(x = PhaseDev, y = amplitude_magnitude_change)) +
      geom_point(alpha = 0.6) +
      geom_smooth(method = "lm", se = FALSE, color = "blue") +
      labs(x = "SJL Magnitude (Hours)", y = "Amplitude Change Mag. (%)") +
      theme_minimal()
      
    # B. Stratified Plot
    plot_stratified_bio <- ggplot(bio_data, aes(x = sjl_severity, y = amplitude_magnitude_change, fill = sjl_severity)) +
      geom_boxplot(alpha = 0.7) +
      labs(x = "SJL Group", y = "Amplitude Change Mag. (%)") +
      theme_minimal() +
      theme(legend.position = "none")
      
    # C. Combined Plot for the current biometric
    combined_bio_plot <- ggarrange(plot_corr_bio, plot_stratified_bio, ncol = 2, nrow = 1)
    bio_plot_annotated <- annotate_figure(combined_bio_plot, top = text_grob(paste("Analysis for", current_bio, "(Group:", group, ")"), face = "bold", size = 14))
    print(bio_plot_annotated)
    
    # Export the combined biometric plot
    plot_filename_bio <- paste0(current_bio, "_Analysis_", gsub("[^A-Za-z0-9]+", "_", group), ".png")
    ggsave(
      file.path(images_output_dir, plot_filename_bio),
      plot = bio_plot_annotated,
      width = 12, height = 6, dpi = 300, bg = "white"
    )
    cat("   > Plot saved for biometric:", current_bio, "\n")
    
    # --- Statistical Tests for Per-Biometric ---
    # A. Continuous Analysis (Correlation)
    correlation_bio <- cor.test(bio_data$PhaseDev, bio_data$amplitude_magnitude_change, method = "spearman")
    power_corr_bio <- pwr.r.test(n = nrow(bio_data), r = correlation_bio$estimate, sig.level = 0.05)$power
    results_list[[length(results_list) + 1]] <- data.frame(age_group = group, biometric = current_bio, test_type = "Correlation", p_value = correlation_bio$p.value, estimate = correlation_bio$estimate, power = power_corr_bio)

    # B. Stratified Analysis (ANOVA)
    anova_bio <- aov(amplitude_magnitude_change ~ sjl_severity, data = bio_data)
    anova_summary_bio <- summary(anova_bio)
    ss_between_bio <- anova_summary_bio[[1]]["sjl_severity", "Sum Sq"]
    ss_within_bio <- anova_summary_bio[[1]]["Residuals", "Sum Sq"]
    f2_bio <- ss_between_bio / ss_within_bio
    power_anova_bio <- pwr.f2.test(u = anova_summary_bio[[1]]["sjl_severity", "Df"], v = anova_summary_bio[[1]]["Residuals", "Df"], f2 = f2_bio, sig.level = 0.05)$power
    results_list[[length(results_list) + 1]] <- data.frame(age_group = group, biometric = current_bio, test_type = "ANOVA", p_value = anova_summary_bio[[1]][1, "Pr(>F)"], estimate = anova_summary_bio[[1]][1, "F value"], power = power_anova_bio)
  }
}

#==============================================================================
# Finalize and Export Results
#==============================================================================
cat("\n\n--- Finalizing and Exporting Statistical Results ---\n")

# Combine all results into the final Jetlag dataframe
if (length(results_list) > 0) {
  Jetlag <- bind_rows(results_list) %>%
    # Round numeric columns for cleaner output
    mutate(across(where(is.numeric), ~round(.x, 4)))
  
  cat("Statistical summary (Jetlag) created:\n")
  print(Jetlag)
  
  # Export the dataframe to an Excel file
  # Note: Assumes a 'valid_path' variable is defined. If not, will save to the working directory.
  if(!exists("valid_path")) valid_path <- getwd()
  export_path <- file.path(valid_path, "Stats", "Social_Jetlag_Statistics.xlsx")
  write.xlsx(Jetlag, export_path, overwrite = TRUE)
  
  cat("\nStatistical results exported to:", export_path, "\n")
  
} else {
  cat("No statistical results were generated.\n")
  Jetlag <- data.frame() # Create empty df if no results
}

cat("\n--- Analysis Complete ---\n")


# Clean up
rm(list = setdiff(ls(), CoreDatasets))
```






#**================================================================**
#** Analysis of Combined Phase Shifts and Deviations w/o Activity  **
#**================================================================**
```{r}
# --- Analysis of Phase Shifts (p_phase and t_phase) ---

# 1. Define helper functions for calculating cyclical differences and variance.

# Calculates the shortest difference between two points on a 24-hour cycle.
calculate_phase_difference <- function(phase1, phase2, cycle_length = 24) {
  diff <- abs(phase1 - phase2)
  pmin(diff, cycle_length - diff)
}

# Calculates circular variance for cyclical data.
circular_variance <- function(x, cycle_length = 24) {
  if (length(na.omit(x)) < 2) return(NA)
  x_rad <- (x / cycle_length) * 2 * pi
  # Calculate mean resultant vector length (R)
  R <- sqrt(sum(cos(x_rad))^2 + sum(sin(x_rad))^2) / length(x)
  1 - R # Return variance
}


# 2. Optimized Pipeline: Prepare data and calculate phase differences in one step.
# The resulting dataframe contains the per-patient, per-biometric phase shifts.
phase_differences <- SJL %>%
  # Filter out 'Both' week type, any rows with NA in 'week', and the 'Steps' biometric
  filter(!is.na(week), week != "Both", bio != "Steps") %>%
  # Handle multiple readings by averaging the phase for each patient, week, and bio
  group_by(patient, week, bio) %>%
  summarise(
    p_phase = mean(p_phase, na.rm = TRUE),
    t_phase = mean(t_phase, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  # Pivot to a wide format to get Weekday and Weekend side-by-side
  pivot_wider(names_from = week, values_from = c(p_phase, t_phase)) %>%
  # This filter removes patients who do not have the core phase data for BOTH
  # Weekday and Weekend, which is the minimum requirement for this analysis.
  filter(!is.na(p_phase_Weekday) & !is.na(p_phase_Weekend) &
         !is.na(t_phase_Weekday) & !is.na(t_phase_Weekend)) %>%
  # Calculate cyclical differences and the total deviation magnitude
  mutate(
    p_phase_diff = calculate_phase_difference(p_phase_Weekday, p_phase_Weekend),
    t_phase_diff = calculate_phase_difference(t_phase_Weekday, t_phase_Weekend),
    magnitude_deviation = p_phase_diff + t_phase_diff
  )

# 3. Create the SJLBIO dataframe with per-patient, per-biometric shifts.
SJLBIO <- phase_differences %>%
  # Select the key columns for the final output
  select(patient, bio, p_phase_diff, t_phase_diff, magnitude_deviation)

cat("\n--- Per-Patient, Per-Biometric Phase Shift Summary (SJLBIO) ---\n")
print(SJLBIO)


# 4. Create the SJLDeviations dataframe with patient-level summary statistics.
SJLDeviations <- phase_differences %>%
  group_by(patient) %>%
  summarise(
    avg_total_deviation = mean(magnitude_deviation, na.rm = TRUE),
    sd_total_deviation = sd(magnitude_deviation, na.rm = TRUE),
    # Calculate circular variance and SD for the deviation magnitude
    circular_variance_deviation = circular_variance(magnitude_deviation),
    # Note: circular_sd requires variance to be < 1, will return NaN otherwise
    circular_sd_deviation = sqrt(-2 * log(1 - circular_variance_deviation)),
    mad_total_deviation = mad(magnitude_deviation, na.rm = TRUE),
    .groups = 'drop'
  )

cat("\n--- Patient-Level Deviation Summary (SJLDeviations) ---\n")
print(SJLDeviations)

# Both 'SJLBIO' and 'SJLDeviations' are now available in your environment.


# --- Correlation of Phase Deviation and Amplitude Deviation (OVERALL & BY BIOMETRIC) ---

# Initialize an empty list to store the results from all analyses
results_list <- list()

# --- Analysis 0: OVERALL Correlation ---
# This calculates the overall amplitude deviation by first calculating the 
# percent difference for each biometric, then averaging those percentages.
cat("\n\n--- Correlation for OVERALL: Phase Deviation vs. Overall Amplitude Deviation ---\n")

amplitude_diffs_overall <- SJL %>%
  filter(!is.na(week), week != "Both", bio != "Steps") %>%
  # Group by patient, week, AND bio to get mean amplitude for each
  group_by(patient, week, bio) %>%
  summarise(mean_amplitude = mean(amplitude, na.rm = TRUE), .groups = 'drop') %>%
  # Pivot to a wide format for comparison
  pivot_wider(names_from = week, values_from = mean_amplitude) %>%
  filter(!is.na(Weekday) & !is.na(Weekend)) %>%
  # Calculate the percentage difference for each biometric
  mutate(percent_diff = abs((Weekend - Weekday) / Weekday) * 100) %>%
  # NOW, group by patient to get a single average percentage difference across their biometrics
  group_by(patient) %>%
  summarise(overall_amplitude_percent_diff = mean(percent_diff, na.rm = TRUE), .groups = 'drop')


# Join the overall amplitude diff with the phase deviation summary
combined_deviation_data_overall <- inner_join(SJLDeviations, amplitude_diffs_overall, by = "patient")

# Perform and store the overall correlations
if (nrow(combined_deviation_data_overall) > 2) {
  # a. Average Deviation vs. Overall Amplitude
  correlation_test_avg_overall <- cor.test(
    combined_deviation_data_overall$avg_total_deviation,
    combined_deviation_data_overall$overall_amplitude_percent_diff,
    method = "spearman"
  )
  print(correlation_test_avg_overall)
  
  plot_avg_overall <- ggplot(combined_deviation_data_overall, aes(x = avg_total_deviation, y = overall_amplitude_percent_diff)) +
    geom_point(alpha = 0.7) + geom_smooth(method = "lm", se = FALSE, color = "blue") +
    labs(title = "Overall Phase vs. Amplitude Deviation", subtitle = "Average Phase Deviation", x = "Average Phase Deviation (Hours)", y = "Overall Amplitude Difference (%)") + theme_minimal()
  print(plot_avg_overall)
  
  n_avg_overall <- nrow(combined_deviation_data_overall)
  rho_avg_overall <- correlation_test_avg_overall$estimate
  power_avg_overall <- pwr.r.test(n = n_avg_overall, r = rho_avg_overall, sig.level = 0.05, alternative = "two.sided")$power
  results_list[[length(results_list) + 1]] <- data.frame(Biometric = "Overall", Analysis_Type = "Phase", p_value = correlation_test_avg_overall$p.value, sample_estimate_rho = rho_avg_overall, power = power_avg_overall)
  
  # b. MAD Deviation vs. Overall Amplitude
  correlation_test_mad_overall <- cor.test(
    combined_deviation_data_overall$mad_total_deviation,
    combined_deviation_data_overall$overall_amplitude_percent_diff,
    method = "spearman"
  )
  print(correlation_test_mad_overall)

  plot_mad_overall <- ggplot(combined_deviation_data_overall, aes(x = mad_total_deviation, y = overall_amplitude_percent_diff)) +
    geom_point(alpha = 0.7) + geom_smooth(method = "lm", se = FALSE, color = "red") +
    labs(title = "Overall Phase vs. Amplitude Deviation", subtitle = "MAD of Phase Deviation", x = "MAD of Phase Deviation (Hours)", y = "Overall Amplitude Difference (%)") + theme_minimal()
  print(plot_mad_overall)
  
  n_mad_overall <- nrow(combined_deviation_data_overall)
  rho_mad_overall <- correlation_test_mad_overall$estimate
  power_mad_overall <- pwr.r.test(n = n_mad_overall, r = rho_mad_overall, sig.level = 0.05, alternative = "two.sided")$power
  results_list[[length(results_list) + 1]] <- data.frame(Biometric = "Overall", Analysis_Type = "MAD", p_value = correlation_test_mad_overall$p.value, sample_estimate_rho = rho_mad_overall, power = power_mad_overall)

} else {
  cat("Not enough combined data to perform overall correlation analysis.\n")
}


# --- Analysis 1-N: Per-Biometric Correlations ---
# This section calculates the amplitude difference for each biometric and then
# correlates it with the patient's overall phase deviation metrics.

amplitude_diffs_by_bio <- SJL %>%
  filter(!is.na(week), week != "Both", bio != "Steps") %>%
  group_by(patient, week, bio) %>%
  summarise(mean_amplitude = mean(amplitude, na.rm = TRUE), .groups = 'drop') %>%
  pivot_wider(names_from = week, values_from = mean_amplitude) %>%
  filter(!is.na(Weekday) & !is.na(Weekend)) %>%
  mutate(amplitude_percent_diff = abs((Weekend - Weekday) / Weekday) * 100) %>%
  select(patient, bio, amplitude_percent_diff)

combined_deviation_data_by_bio <- inner_join(SJLDeviations, amplitude_diffs_by_bio, by = "patient")
biometrics_to_analyze <- unique(combined_deviation_data_by_bio$bio)

for (current_bio in biometrics_to_analyze) {
  
  bio_data <- combined_deviation_data_by_bio %>% filter(bio == current_bio)
  
  # a. Average Phase Deviation vs. Amplitude Deviation
  cat(paste("\n--- Correlation for", current_bio, ": Average Phase Deviation vs. Amplitude Deviation ---\n"))
  
  if (nrow(bio_data) > 2) {
    correlation_test_avg <- cor.test(bio_data$avg_total_deviation, bio_data$amplitude_percent_diff, method = "spearman")
    print(correlation_test_avg)
    
    plot_avg <- ggplot(bio_data, aes(x = avg_total_deviation, y = amplitude_percent_diff)) +
      geom_point(alpha = 0.7) + geom_smooth(method = "lm", se = FALSE, color = "blue") +
      labs(title = paste("Phase vs. Amplitude Deviation for", current_bio), subtitle = "Average Phase Deviation", x = "Average Phase Deviation (Hours)", y = "Amplitude Difference (%)") + theme_minimal()
    print(plot_avg)
    
    n_avg <- nrow(bio_data)
    rho_avg <- correlation_test_avg$estimate
    power_avg <- pwr.r.test(n = n_avg, r = rho_avg, sig.level = 0.05, alternative = "two.sided")$power
    results_list[[length(results_list) + 1]] <- data.frame(Biometric = current_bio, Analysis_Type = "Phase", p_value = correlation_test_avg$p.value, sample_estimate_rho = rho_avg, power = power_avg)
    
  } else {
    cat(paste("Not enough data for", current_bio, "to perform correlation for average deviation.\n"))
  }
  
  # b. MAD of Phase Deviation vs. Amplitude Deviation
  cat(paste("\n--- Correlation for", current_bio, ": MAD of Phase Deviation vs. Amplitude Deviation ---\n"))
  
  if (nrow(bio_data) > 2) {
    correlation_test_mad <- cor.test(bio_data$mad_total_deviation, bio_data$amplitude_percent_diff, method = "spearman")
    print(correlation_test_mad)
    
    plot_mad <- ggplot(bio_data, aes(x = mad_total_deviation, y = amplitude_percent_diff)) +
      geom_point(alpha = 0.7) + geom_smooth(method = "lm", se = FALSE, color = "red") +
      labs(title = paste("Phase vs. Amplitude Deviation for", current_bio), subtitle = "MAD of Phase Deviation", x = "MAD of Phase Deviation (Hours)", y = "Amplitude Difference (%)") + theme_minimal()
    print(plot_mad)
    
    n_mad <- nrow(bio_data)
    rho_mad <- correlation_test_mad$estimate
    power_mad <- pwr.r.test(n = n_mad, r = rho_mad, sig.level = 0.05, alternative = "two.sided")$power
    results_list[[length(results_list) + 1]] <- data.frame(Biometric = current_bio, Analysis_Type = "MAD", p_value = correlation_test_mad$p.value, sample_estimate_rho = rho_mad, power = power_mad)
    
  } else {
    cat(paste("Not enough data for", current_bio, "to perform correlation for MAD deviation.\n"))
  }
}


# --- Compile and Export Statistical Analysis Results ---

# Create the DeviationsS dataframe from the list of results after all analyses.
if (length(results_list) > 0) {
  DeviationsS <- bind_rows(results_list)
  
  cat("\n\n--- Summary of Statistical Analyses (DeviationsS) ---\n")
  print(DeviationsS)
  
  cat("\nAnalysis complete.\n")
  
} else {
  cat("\n\n--- Could not generate statistical summary as no correlation tests were successful. ---\n")
  DeviationsS <- data.frame() # Create an empty dataframe if no results
}




# Clean up
rm(list = setdiff(ls(), CoreDatasets))

```





