---
title: "Phase 2 Misc Stats"
output: html_notebook
Step: 5
---


#**================================================================**
#** Libraries and Environment Setup                  **
#**================================================================**
```{r}
#** Load necessary libraries *
# Using pacman to install and load packages in one step
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  # Original Libraries
  dplyr,          # For data manipulation
  tidyr,          # For data tidying
  openxlsx,       # For reading/writing Excel files
  lubridate,      # For easier date-time manipulation
  data.table,     # For efficient data handling, especially rleid
  pracma,         # For findpeaks
  lomb,           # For periodogram
  broom,          # For cleaning t-tests
  GLMMcosinor,    # For generalized linear mixed cosinor models
  circacompare,   # For comparing circadian rhythms
  tidyverse,      # A collection of R packages for data science
  brms,           # For Bayesian regression models using Stan
  rstanarm,       # For Bayesian models via RStan
  paletteer,      # Provides a collection of color palettes
  ggcorrplot,     # For visualizing correlation matrices
  ggpubr,         # For publication-ready plots
  corrr,          # For exploring correlations
  qgraph,         # For network analysis and visualization
  combinat,       # For combinatorics
  zoo,            # For ordered time series data
  caret,          # For classification and regression training
  janitor,        # For simple data cleaning
  pwr,            # For power analysis
  lmPerm,         # For permutation tests for linear models
  mgcv,            # For permutation tests for GAM
  pwr,
  rstatix,
  hms,
  fs,
  car,
)

#** --- Set up a valid path --- *
# Define base paths for both possible directories
base_paths <- c(
  "E:/OneDrive/TUNCOM/TUNCRG/06. Phase 2 Data/Aging",
  "C:/Users/samue/OneDrive/TUNCOM/TUNCRG/06. Phase 2 Data/Aging"
)

# Find the first existing directory
valid_path <- first(base_paths[dir.exists(base_paths)])

if (is.na(valid_path)) {
  stop("Neither of the specified base directories exists. Please check the paths.")
}

#** --- Define objects to keep --- *
# This list helps in managing the global environment
CoreDatasets <- c(
"CorsanoAnalysismulti", "CorsanoAnalysissingle", "CorsanoAnalysisSleepexpand", "SleepAnalysis", "StatS", "CoreDatasets", "subjects", "SplitModel2", "Statistics", "biomarkers", "SleepStat", "Analysis", "CorsanoAnalysissplit", "valid_path", "processed_subjects", "Stat", "processed_subjects1", "processed_subjects2", "processed_subjects3", "CorsanoAnalysisAll", "Shiftwork", "Shiftwork2", "ShiftStat", "Sleepwork", "CorsanoAnalysisSleepmulti", "CorsanoAnalysisSleepsingle", "CorsanoAnalysisWave", "PhaseDiff", "SLEEP", "CorsanoShiftWave", "Variability", "Stability", "SJL", "StatSS", "SLEEP1", "AmpMesAge", "AmpMesGen", "BioBmiStats", "DeviationsS", "SJLDeviations", "SJLBIO", "jsl_summary", "Jetlag", "biolist", "PhysCog", "Aging", "AgingA", "SJL2", "SJLBio","StatSSS", "TTest"
)

# Biolist
biolist <- c("HR", "Steps", "Energy", "Breath", "HRV", "RR", "Cortisol", "Stress", "SBT", "CBT")


# Clean up
rm(list = setdiff(ls(), CoreDatasets))
```


#** Are the CBT rhythms statistically different **#
```{r}
Comp1 <- CorsanoAnalysismulti %>%
  filter(Subject == c("BWFD6Z76","A32VTWXQ"),
         Day != c("Sunday", "Saturday"))

Comp2 <- CorsanoAnalysismulti %>%
  filter(Subject == c("BWFD6Z76","RJ43K3DS"),
         Day != c("Sunday", "Saturday"))


Comp3 <- CorsanoAnalysismulti %>%
  filter(Subject == c("RJ43K3DS","A32VTWXQ"),
         Day != c("Sunday", "Saturday"))



results <- circacompare(
  x = Comp1,
  col_time = "Time",
  col_group = "Subject",
  col_outcome = "CBT",
  period = 24
)

results1 <- circacompare(
  x = Comp2,
  col_time = "Time",
  col_group = "Subject",
  col_outcome = "CBT",
  period = 24
)

results2 <- circacompare(
  x = Comp3,
  col_time = "Time",
  col_group = "Subject",
  col_outcome = "CBT",
  period = 24
)



results3 <- circacompare(
  x = Comp1,
  col_time = "Time",
  col_group = "Subject",
  col_outcome = "Steps",
  period = 24
)

results4 <- circacompare(
  x = Comp2,
  col_time = "Time",
  col_group = "Subject",
  col_outcome = "Steps",
  period = 24
)

results5 <- circacompare(
  x = Comp3,
  col_time = "Time",
  col_group = "Subject",
  col_outcome = "Steps",
  period = 24
)


results
results1
results2
results3
results4
results5
```



#** Quantifying the slopes and FWHM
```{r}
# 1. Define the morphology extraction function
calculate_morphology_metrics <- function(df, x_col = "Time", y_col = "CosineValue") {
  
  # Ensure the target column exists
  if (!y_col %in% names(df)) {
    return(data.frame(
      FWHM_hours = NA,
      Max_Ascending_Slope = NA,
      Max_Descending_Slope = NA
    ))
  }

  # Sort by time to ensure sequential differences
  df <- df[order(df[[x_col]]), ]
  
  # Calculate slopes using the full 48-hour data
  t_full <- df[[x_col]]
  y_full <- df[[y_col]]
  
  dy <- diff(y_full)
  dt <- diff(t_full)
  
  # Prevent division by zero
  dt[dt == 0] <- NA 
  slopes <- dy / dt
  
  # Handle cases where slopes might be all NA to prevent warnings
  if(all(is.na(slopes))) {
     max_asc_slope <- NA
     max_desc_slope <- NA
  } else {
     max_asc_slope <- max(slopes, na.rm = TRUE)
     max_desc_slope <- min(slopes, na.rm = TRUE)
  }
  
  # Isolate the first 24 hours to cleanly calculate one peak's FWHM
  df_24h <- df[df[[x_col]] <= 24, ]
  t <- df_24h[[x_col]]
  y <- df_24h[[y_col]]
  
  # Calculate FWHM thresholds
  if(all(is.na(y))) {
     fwhm <- NA
  } else {
      max_y <- max(y, na.rm = TRUE)
      min_y <- min(y, na.rm = TRUE)
      half_max <- min_y + (max_y - min_y) / 2
      
      # Normalize the curve around the half-maximum threshold
      y_shifted <- y - half_max
      
      # Identify indices where the curve crosses the half-maximum
      crossings <- which(diff(sign(y_shifted)) != 0)
      
      crossing_times <- numeric(length(crossings))
      
      # Linearly interpolate the exact crossing time for precision
      for (i in seq_along(crossings)) {
        idx <- crossings[i]
        t0 <- t[idx]; t1 <- t[idx+1]
        y0 <- y_shifted[idx]; y1 <- y_shifted[idx+1]
        
        # Avoid division by zero
        if ((y1 - y0) != 0) {
          crossing_times[i] <- t0 - y0 * (t1 - t0) / (y1 - y0)
        } else {
          crossing_times[i] <- t0
        }
      }
      
      # Calculate FWHM
      fwhm <- NA
      if (length(crossing_times) >= 2) {
        fwhm <- abs(crossing_times[2] - crossing_times[1])
      }
  }
  
  # Output the results
  return(data.frame(
    FWHM_hours = fwhm,
    Max_Ascending_Slope = max_asc_slope,
    Max_Descending_Slope = max_desc_slope
  ))
}

# 2. Reshape the data to create the 'Bio' column
# This finds all columns ending in "Cosine" (like CBTCosine, HRCosine)
# It strips "Cosine" to make the "Bio" column, and puts the values in "CosineValue"
long_wave <- CorsanoAnalysisWave %>%
  pivot_longer(
    cols = ends_with("Cosine"), 
    names_to = "Bio",
    names_pattern = "(.*)Cosine", 
    values_to = "CosineValue"
  ) %>%
  filter(!is.na(CosineValue)) # Optional: removes empty rows to speed up processing

# 3. Apply the function across all combinations
morphology_results <- long_wave %>%
  group_by(Subject, Week, Bio) %>%
  group_modify(~ calculate_morphology_metrics(.x, x_col = "Time", y_col = "CosineValue")) %>%
  ungroup()

# 4. Merge into the Stat dataframe
# Aligns "Patient" to "Subject" and "week" to "week"
morphology_results <- morphology_results %>%
  rename(week = Week)

StatSSS <- StatSS %>%
  left_join(morphology_results, by = c("Patient" = "Subject", "week" = "week", "Bio" = "Bio"))


# 5. Export
# Assuming Stat_Combined is supposed to be StatSSS
export_path <- paste0(valid_path, "/Stats/StatSSS.xlsx")
write.xlsx(StatSSS, export_path, rowNames = FALSE, firstRow = TRUE)
```



#** Measuring Period
```{r}
# 1. Filter the dataset as requested
temp2 <- CorsanoAnalysissplit %>%
  filter(Week == "Weekday")

# 2. Sequentialize the Time variable (Weekdays only)
# Removed Saturday and Sunday from offsets
day_offsets <- c("Monday" = 0, "Tuesday" = 24, "Wednesday" = 48, 
                 "Thursday" = 72, "Friday" = 96)

# Enforce Weekday filtering, remove Time == 24, and calculate Cumulative_Time
temp2_seq <- temp2 %>%
  filter(!is.na(Day)) %>%
  filter(Time < 24) %>% # Truncates the day at 23.833
  mutate(Day = factor(Day, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))) %>%
  arrange(Subject, Day, Time) %>%
  mutate(Cumulative_Time = Time + day_offsets[as.character(Day)])

# 3. Initialize an empty dataframe to store the period estimates
# Updated 'Biomarker' to 'Bio' and changed 'Period' to character to accept "Error"
period_results <- data.frame(Subject = character(),
                             Bio = character(),
                             Period = character(),
                             P_Value = numeric(),
                             stringsAsFactors = FALSE)

# 4. Execute the nested loop for Subjects and Biomarkers
subjects <- unique(temp2_seq$Subject)

for (sub in subjects) {
  # Subset data for the current subject
  sub_data <- temp2_seq %>% filter(Subject == sub)
  
  for (bio in biolist) {
    # Isolate time and the specific biomarker, removing NAs
    clean_data <- sub_data %>%
      select(Cumulative_Time, all_of(bio)) %>%
      na.omit()
    
    # Run periodogram if there is sufficient data (e.g., > 10 valid data points)
    if (nrow(clean_data) > 10) {
      lomb_res <- lsp(clean_data[[bio]], times = clean_data$Cumulative_Time, 
                      from = 12, to = 36, type = "period", plot = FALSE)
      
      p_val <- lomb_res$p.value
      
      # Conditional logic to check p-value significance
      if (p_val > 0.05) {
        dom_period <- "Error"
      } else {
        dom_period <- as.character(lomb_res$peak.at[1])
      }
      
    } else {
      dom_period <- NA 
      p_val <- NA # Assign NA if insufficient data to avoid errors
    }
    
    # Append the results to the storage dataframe
    period_results <- rbind(period_results, 
                            data.frame(Subject = sub, 
                                       Bio = bio, 
                                       Period = dom_period,
                                       P_Value = p_val,
                                       stringsAsFactors = FALSE)) 
  }
}

period_results <- period_results %>%
  select("Subject", "Bio","Period")



StatSSS <- StatSSS %>%
  left_join(period_results, by = c("Patient" = "Subject", "Bio" = "Bio"))


# 5. Export
# Assuming Stat_Combined is supposed to be StatSSS
export_path <- paste0(valid_path, "/Stats/StatSSS.xlsx")
write.xlsx(StatSSS, export_path, rowNames = FALSE, firstRow = TRUE)

```


#** Stat Analysis of Period and Phase 
```{r}
# Settting Age Groups
filtered_data <- StatSSS %>%
  filter(week == "Weekday") %>%
  mutate(AgeGroup = case_when(
    age <= 40 ~ "Young",
    age >= 60 ~ "Old",
    TRUE ~ NA_character_ # This assigns NA to anyone aged 41-59
    )) %>%
  filter(!is.na(AgeGroup))


# Reshaping Dataframe
long_data <- filtered_data %>%
  mutate(across(c(Amplitude, Mesor, Period, PPhase, TPhase), as.numeric)) %>%
  pivot_longer(
    cols = c(Amplitude, Mesor, Period, PPhase, TPhase),
    names_to = "Metric",
    values_to = "Value"
  ) %>%
  filter(!is.na(Value))


# T-Testing
t_test_results <- long_data %>%
  group_by(Bio, Metric) %>%
  filter(sum(AgeGroup == "Young") >= 2 & sum(AgeGroup == "Old") >= 2) %>%
  group_modify(~ broom::tidy(t.test(Value ~ AgeGroup, data = .x))) %>%
  ungroup()
  


#Renaming:
TTest <- t_test_results %>%
  rename(
    difference = estimate,
    Old = estimate1,
    Young = estimate2
  ) %>%
  select(-c(method, alternative, statistic, parameter)) %>%
  # Add the boolean column for significance using an alpha of 0.05
  mutate(Significant = p.value < 0.05)



# 5. Export
# Assuming Stat_Combined is supposed to be StatSSS
export_path <- paste0(valid_path, "/Stats/TTests.xlsx")
write.xlsx(TTest, export_path, rowNames = FALSE, firstRow = TRUE)

```






#** Mid point of sleep/activity vs midpoint/low of CBT**#
```{r}
#*** Positive TPhase ***
# --- STEP 2: The Corrected Pipeline ---
StatisticsA <- StatSS %>%
  # FIX 1: Filter BEFORE pivoting. 
  filter(week == "Weekday",
         Bio == "CBT")
   

#** Amplitude Energy vs CBT
cor.test(StatisticsA$midrange, StatisticsA$MP)
summary(lm(midrange ~ MP, data = StatisticsA))
ggscatter(StatisticsA, x = "MP", y = "midrange", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "mid point of sleep", ylab = "average nadir")
```





#*** CBT, Energy, Activity Amplitude **
```{r}
#** Amplitude Energy vs CBT
cor.test(Statistics$Energyamp, Statistics$CBTamp)
summary(lm(Energyamp ~ CBTamp, data = Statistics))
ggscatter(Statistics, x = "CBTamp", y = "Energyamp", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CBT Amplitude", ylab = "Energy Amplitude")



#** Amplitude CBT vs Steps
cor.test(Statistics$Stepsamp, Statistics$CBTamp)
summary(lm(Stepsamp ~ CBTamp, data = Statistics))
ggscatter(Statistics, x = "CBTamp", y = "Stepsamp", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CBT Amplitude", ylab = "Activity Amplitude")



#*** CBT, Energy, Activity Phase **


#** Amplitude Energy vs Steps **
cor.test(Statistics$EnergyPPhase, Statistics$StepsPPhase)
summary(lm(EnergyPPhase ~ StepsPPhase, data = Statistics))

ggscatter(Statistics, x = "StepsPPhase", y = "EnergyPPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Activity Peak Phase", ylab = "Energy Peak Phase")


cor.test(StatisticsS$EnergyTPhase, StatisticsS$StepsTPhase)
summary(lm(EnergyTPhase ~ StepsTPhase, data = StatisticsS))
ggscatter(StatisticsS, x = "StepsTPhase", y = "EnergyTPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Activity Trouph Phase", ylab = "Energy Trouph Phase")




#** Amplitude Energy vs CBT **
cor.test(Statistics$EnergyPPhase, Statistics$CBTPPhase)
summary(lm(EnergyPPhase ~ CBTPPhase, data = Statistics))
ggscatter(Statistics, x = "CBTPPhase", y = "EnergyPPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CBT Peak Phase", ylab = "Energy Peak Phase")


cor.test(StatisticsS$EnergyTPhase, StatisticsS$CBTTPhase)
summary(lm(EnergyTPhase ~ CBTTPhase, data = StatisticsS))
ggscatter(StatisticsS, x = "CBTTPhase", y = "EnergyTPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CBT Trouph Phase", ylab = "Energy Trouph Phase")



#** Amplitude CBT vs Steps **
cor.test(Statistics$StepsPPhase, Statistics$CBTPPhase)
summary(lm(StepsPPhase ~ CBTPPhase, data = Statistics))

ggscatter(Statistics, x = "CBTPPhase", y = "StepsPPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CBT Peak Phase", ylab = "Activity Peak Phase")



cor.test(StatisticsS$StepsTPhase, StatisticsS$CBTTPhase)
summary(lm(StepsTPhase ~ CBTTPhase, data = StatisticsS))

ggscatter(StatisticsS, x = "CBTTPhase", y = "StepsTPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CBT Trouph Phase", ylab = "Activity Trouph Phase")
```





#*** HRV, Energy, Activity ***
```{r}

#*** HRV, CBT, Energy, Activity Amplitude **

#* HRV vs CBT *#
cor.test(Statistics$CBTamp, Statistics$HRVamp)
summary(lm(CBTamp ~ HRVamp, data = Statistics))

ggscatter(Statistics, x = "HRVamp", y = "CBTamp", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "HRV Amplitude", ylab = "CBT Amplitude")


#* HRV vs Energy *#
cor.test(Statistics$Energyamp, Statistics$HRVamp)
summary(lm(Energyamp ~ HRVamp, data = Statistics))

ggscatter(Statistics, x = "HRVamp", y = "Energyamp", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "HRV Amplitude", ylab = "Energy Amplitude")


#* HRV vs Activity *#
cor.test(Statistics$Stepsamp, Statistics$HRVamp)
summary(lm(Stepsamp ~ HRVamp, data = Statistics))

ggscatter(Statistics, x = "HRVamp", y = "Stepsamp", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "HRV Amplitude", ylab = "Activity Amplitude")



#*** HRV, CBT, Energy, Activity Phase**

#* HRV vs CBT *#
cor.test(Statistics$CBTPPhase, Statistics$HRVPPhase)
summary(lm(CBTPPhase ~ HRVPPhase, data = Statistics))
ggscatter(Statistics, x = "HRVPPhase", y = "CBTPPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "HRV Peak Phase", ylab = "CBT Peak Phase")


cor.test(StatisticsS$CBTTPhase, StatisticsS$HRVTPhase)
summary(lm(CBTTPhase ~ HRVTPhase, data = StatisticsS))
ggscatter(StatisticsS, x = "HRVTPhase", y = "CBTTPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "HRV Trouph Phase", ylab = "CBT Trouph Phase")




#* HRV vs Energy *#
cor.test(Statistics$EnergyPPhase, Statistics$HRVPPhase)
summary(lm(EnergyPPhase ~ HRVPPhase, data = Statistics))
ggscatter(Statistics, x = "HRVPPhase", y = "EnergyPPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "HRV Peak Phase", ylab = "Energy Peak Phase")


cor.test(StatisticsS$EnergyTPhase, StatisticsS$HRVTPhase)
summary(lm(EnergyTPhase ~ HRVTPhase, data = StatisticsS))
ggscatter(StatisticsS, x = "HRVTPhase", y = "EnergyTPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "HRV Trouph Phase", ylab = "Energy Trouph Phase")



#* HRV vs Activity *#
cor.test(Statistics$StepsPPhase, Statistics$HRVPPhase)
summary(lm(StepsPPhase ~ HRVPPhase, data = Statistics))
ggscatter(Statistics, x = "HRVPPhase", y = "StepsPPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "HRV Peak Phase", ylab = "Activity Peak Phase")


cor.test(StatisticsS$StepsTPhase, StatisticsS$HRVTPhase)
summary(lm(StepsTPhase ~ HRVTPhase, data = StatisticsS))
ggscatter(StatisticsS, x = "HRVTPhase", y = "StepsTPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "HRV Trouph Phase", ylab = "Activity Trouph Phase")

```





#*** Breath, CBT, Energy, Activity ***#
```{r}

#*** Breath, CBT, Energy, Activity Amplitude **

#* Breath vs CBT *#
cor.test(Statistics$CBTamp, Statistics$Breathamp)
summary(lm(CBTamp ~ Breathamp, data = Statistics))

ggscatter(Statistics, x = "Breathamp", y = "CBTamp", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Respiratory Rate Amplitude", ylab = "CBT Amplitude")


#* Breath vs Energy *#
cor.test(Statistics$Energyamp, Statistics$Breathamp)
summary(lm(Energyamp ~ Breathamp, data = Statistics))

ggscatter(Statistics, x = "Breathamp", y = "Energyamp", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
         xlab = "Respiratory Rate Amplitude", ylab = "Energy Amplitude")


#* Breath vs Activity *#
cor.test(Statistics$Stepsamp, Statistics$Breathamp)
summary(lm(Stepsamp ~ Breathamp, data = Statistics))

ggscatter(Statistics, x = "Breathamp", y = "Stepsamp", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Respiratory Rate Amplitude", ylab = "Activity Amplitude")



#*** Breath, CBT, Energy, Activity Phase**

#* Breath vs CBT *#
cor.test(Statistics$CBTPPhase, Statistics$BreathPPhase)
summary(lm(CBTPPhase ~ BreathPPhase, data = Statistics))
ggscatter(Statistics, x = "BreathPPhase", y = "CBTPPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Breath Peak Phase", ylab = "CBT Peak Phase")


cor.test(StatisticsS$CBTTPhase, StatisticsS$BreathTPhase)
summary(lm(CBTTPhase ~ BreathTPhase, data = StatisticsS))
ggscatter(StatisticsS, x = "BreathTPhase", y = "CBTTPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Respiratory Rate Trouph Phase", ylab = "CBT Trouph Phase")



#* Breath vs Activity *#
cor.test(Statistics$StepsPPhase, Statistics$BreathPPhase)
summary(lm(StepsPPhase ~ BreathPPhase, data = Statistics))
ggscatter(Statistics, x = "BreathPPhase", y = "StepsPPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Respiratory Rate Peak Phase", ylab = "Activity Peak Phase")


cor.test(StatisticsS$StepsTPhase, StatisticsS$BreathTPhase)
summary(lm(StepsTPhase ~ BreathTPhase, data = StatisticsS))
ggscatter(StatisticsS, x = "BreathTPhase", y = "StepsTPhase", 
          add = "reg.line", conf.int = TRUE, 
          add.params = list(color = "blue", fill = "darkgray"),
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Respiratory Rate Trouph Phase", ylab = "Activity Trouph Phase")

```




#*** Social Jetlag ***
```{r}
# Create a separate dataframe for this analysis, filtering for only Weekday and Weekend
# Add age group stratification
SJLA <- SJL %>%
  filter(week %in% c("Weekday", "Weekend")) %>%
  mutate(age_group = cut(age,
                         breaks = c(19, 40, 70, Inf),
                         labels = c("20-40", "41-70", "71+"),
                         include.lowest = TRUE))

# Helper Function: Calculate Circular Difference (Absolute)
calculate_phase_difference <- function(phase1, phase2, cycle_length = 24) {
  diff <- abs(phase1 - phase2)
  pmin(diff, cycle_length - diff)
}


#==============================================================================
# Step 1 & 2: Calculate and Stratify Social Jetlag
#==============================================================================
cat("--- Step 1 & 2: Calculating and stratifying Social Jetlag ---\n")

sjl_summary <- SJLA %>%
  group_by(patient, week) %>%
  summarise(mean_mp = mean(p_phase, na.rm = TRUE), .groups = 'drop') %>%
  pivot_wider(names_from = week, values_from = mean_mp) %>%
  filter(!is.na(Weekday) & !is.na(Weekend)) %>%
  mutate(PhaseDev = calculate_phase_difference(Weekday, Weekend)) %>%
  mutate(sjl_severity = cut(PhaseDev,
                            breaks = c(-Inf, 1, 2, Inf),
                            labels = c("Mild (0-1h)", "Moderate (1-2h)", "Severe (2+h)"),
                            right = TRUE)) %>%
  select(patient, PhaseDev, sjl_severity)

# Add age group information to the main summary table
patient_info <- SJLA %>% distinct(patient, age_group)
sjl_summary <- inner_join(sjl_summary, patient_info, by = "patient")

cat("Social Jetlag summary created for", nrow(sjl_summary), "patients.\n")


#==============================================================================
# NEW: Histogram of Social Jetlag Distribution
#==============================================================================
cat("\n--- Generating Histogram of Phase Deviations ---\n")

# Assumes valid_path exists, otherwise uses getwd()
if(!exists("valid_path")) valid_path <- getwd()
images_output_dir <- file.path(valid_path, "Stats", "Images", "Jetlag")
if (!dir.exists(images_output_dir)) dir.create(images_output_dir, recursive = TRUE)

# Generate Histogram
hist_plot <- ggplot(sjl_summary, aes(x = PhaseDev)) +
  geom_histogram(binwidth = 0.5, fill = "steelblue", color = "white", alpha = 0.8) +
  geom_vline(aes(xintercept = mean(PhaseDev, na.rm=TRUE)), color="red", linetype="dashed", size=1) +
  labs(title = "Distribution of Social Jetlag (Phase Deviation)",
       subtitle = paste("Mean deviation:", round(mean(sjl_summary$PhaseDev, na.rm=TRUE), 2), "hours"),
       x = "Phase Deviation (Hours)",
       y = "Count of Patients") +
  theme_minimal()

# Save Histogram
ggsave(file.path(images_output_dir, "SJL_Distribution_Histogram.png"), 
       plot = hist_plot, width = 8, height = 6, bg = "white")

print(hist_plot)
cat("Histogram saved.\n")


#==============================================================================
# Step 3: Evaluate Weekday vs. Weekend Rhythm Changes
#==============================================================================
cat("\n--- Step 3: Calculating rhythm changes from Weekday to Weekend ---\n")

rhythm_changes_by_bio <- SJLA %>%
  group_by(patient, week, bio) %>%
  summarise(across(c(amplitude, mesor), ~mean(.x, na.rm = TRUE)), .groups = 'drop') %>%
  pivot_wider(names_from = week, values_from = c(amplitude, mesor)) %>%
  filter(if_all(starts_with(c("amplitude_", "mesor_")), ~!is.na(.))) %>%
  mutate(
    amplitude_directed_change = ((amplitude_Weekend - amplitude_Weekday) / amplitude_Weekday) * 100,
    amplitude_magnitude_change = abs(amplitude_directed_change)
  )

overall_amplitude_changes <- rhythm_changes_by_bio %>%
  group_by(patient) %>%
  summarise(
    overall_amplitude_directed_change = mean(amplitude_directed_change, na.rm = TRUE),
    overall_amplitude_magnitude_change = mean(amplitude_magnitude_change, na.rm = TRUE)
  )

#==============================================================================
# Main Analysis Loop (Modified for Boxplots + Significance Only)
#==============================================================================
cat("\n--- Generating Boxplots with Significance ---\n")

results_list <- list()
analysis_groups <- c("Overall", levels(SJLA$age_group))

# Define comparisons for the significance brackets
# These must match your 'labels' in the cut function exactly
my_comparisons <- list( 
  c("Mild (0-1h)", "Moderate (1-2h)"), 
  c("Moderate (1-2h)", "Severe (2+h)"), 
  c("Mild (0-1h)", "Severe (2+h)") 
)

for(group in analysis_groups) {
  
  # Filter data for the current group
  if (group == "Overall") {
    current_sjl_summary <- sjl_summary
  } else {
    current_sjl_summary <- sjl_summary %>% filter(age_group == group)
  }
  
  # Check for sufficient data
  if(nrow(current_sjl_summary) < 3) {
    next 
  }
  
  # Join data
  analysis_data <- inner_join(current_sjl_summary, overall_amplitude_changes, by = "patient")
  
  # --- Visualization: Boxplot with Significance ---
  
  # Create Boxplot
  # Note: method = "t.test" or "wilcox.test" can be used. 
  # "p.signif" gives asterisks (*), "p.format" gives numbers.
  plot_stratified_overall <- ggplot(analysis_data, aes(x = sjl_severity, y = overall_amplitude_magnitude_change, fill = sjl_severity)) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA) + # Hide outliers if adding jitter, otherwise keep
    geom_jitter(width = 0.2, alpha = 0.3) + # Adds points to show data distribution
    stat_compare_means(comparisons = my_comparisons, method = "t.test", label = "p.signif") + # Adds the brackets
    stat_compare_means(label.y = max(analysis_data$overall_amplitude_magnitude_change) * 1.1) + # Adds global p-value
    labs(title = paste("Overall Amplitude Change by SJL Severity -", group), 
         x = "SJL Group", 
         y = "Overall Amplitude Change Mag. (%)") +
    theme_minimal() +
    theme(legend.position = "none")
  
  print(plot_stratified_overall)
  
  # Export the plot
  plot_filename_overall <- paste0("Boxplot_SJL_vs_Amp_", gsub("[^A-Za-z0-9]+", "_", group), ".png")
  ggsave(
    file.path(images_output_dir, plot_filename_overall),
    plot = plot_stratified_overall,
    width = 8, height = 6, dpi = 300, bg = "white"
  )
  cat(" > Boxplot saved for group:", group, "\n")
  
  # --- Statistics (Keep ANOVA for the Excel sheet) ---
  anova_overall <- aov(overall_amplitude_magnitude_change ~ sjl_severity, data = analysis_data)
  anova_summary <- summary(anova_overall)
  
  # Power calculation
  ss_between <- anova_summary[[1]]["sjl_severity", "Sum Sq"]
  ss_within <- anova_summary[[1]]["Residuals", "Sum Sq"]
  f2 <- ss_between / ss_within
  power_anova_overall <- pwr.f2.test(u = anova_summary[[1]]["sjl_severity", "Df"], 
                                     v = anova_summary[[1]]["Residuals", "Df"], 
                                     f2 = f2, sig.level = 0.05)$power
  
  results_list[[length(results_list) + 1]] <- data.frame(
    age_group = group, 
    biometric = "Overall", 
    test_type = "ANOVA", 
    p_value = anova_summary[[1]][1, "Pr(>F)"], 
    estimate = anova_summary[[1]][1, "F value"], 
    power = power_anova_overall
  )
}


cat("\n--- Analysis Complete ---\n")
rm(list = setdiff(ls(), CoreDatasets))

```



#** Variability **#
```{r}
#==============================================================================
# NEW: Histogram of Variability (MAD) Distribution
#==============================================================================

StatSJL <- StatSS %>%
  select(Patient, week, MAD) %>%
  filter(week == "Weekday") %>%
  distinct(Patient, .keep_all=TRUE)


# Generate Histogram
hist_plot <- ggplot(StatSJL, aes(x = MAD)) +
  geom_histogram(binwidth = 10, fill = "steelblue", color = "white", alpha = 0.8) +
  geom_vline(aes(xintercept = mean(MAD, na.rm=TRUE)), color="red", linetype="dashed", size=1) +
  labs(title = "Distribution of Circadian Stability (Mean Absolute Deviation)",
       subtitle = paste("Mean deviation:", round(mean(StatSJL$MAD, na.rm=TRUE), 2), "minutes"),
       x = "Phase Deviation (Minutes)",
       y = "Count of Patients") +
  theme_minimal()

# Save Histogram
#ggsave(file.path(images_output_dir, "SJL_Distribution_Histogram.png"), 
 #      plot = hist_plot, width = 8, height = 6, bg = "white")

print(hist_plot)
```

#** Variability **#
```{r}
#==============================================================================
# NEW: Histogram of Variability (MAD) Distribution
#==============================================================================

StatSJL <- StatSS %>%
  select(Patient, week, MAD, age) %>%
  filter(week == "Weekday") %>%
  distinct(Patient, .keep_all=TRUE) %>%
  filter(age < 40)


# Generate Histogram
hist_plot <- ggplot(StatSJL, aes(x = MAD)) +
  geom_histogram(binwidth = 10, fill = "steelblue", color = "white", alpha = 0.8) +
  geom_vline(aes(xintercept = mean(MAD, na.rm=TRUE)), color="red", linetype="dashed", size=1) +
  labs(title = "Distribution of Circadian Stability (Mean Absolute Deviation)",
       subtitle = paste("Mean deviation:", round(mean(StatSJL$MAD, na.rm=TRUE), 2), "minutes"),
       x = "Phase Deviation (Minutes)",
       y = "Count of Patients") +
  theme_minimal()

# Save Histogram
#ggsave(file.path(images_output_dir, "SJL_Distribution_Histogram.png"), 
 #      plot = hist_plot, width = 8, height = 6, bg = "white")

print(hist_plot)
```






```{r}

unique(CorsanoAnalysismulti$Subject)

Subject3 <- "WJAQEYA8"
```


```{r}
# ==========================================
# 1. Load and Filter Data
# ==========================================
# Assuming 'CorsanoAnalysismulti' is loaded in your R environment
df <- CorsanoAnalysismulti %>%
  filter(Subject == Subject3)

# DATA CHECK:
if("Steps" %in% names(df)) {
  # Renaming Energy to activity for consistency
  df <- rename(df, activity = Energy)
} else {
  stop("Column 'Steps' not found. Please ensure the dataframe has a 'Steps' column.")
}

# ==========================================
# 1.1 Calculate and Subtract Baseline (NEW STEP)
# ==========================================
# Calculate the average baseline of Energy across the whole dataset
avg_baseline <- mean(df$activity, na.rm = TRUE)

# Subtract the baseline from the activity.
# pmax(0, ...) ensures that if activity < baseline, the result is 0 (no negative bars)
df <- df %>%
  mutate(activity_adjusted = pmax(0, activity - avg_baseline))

# ==========================================
# 2. Data Processing for Double Plotting
# ==========================================
# Logic Update:
# The 'Time' column is cumulative (e.g., 27.0 = 3 AM on Day 2).

actigram_data <- df %>%
  mutate(
    # Ensure Time is numeric
    raw_time = as.numeric(Time),
    
    # Calculate Day Index: 
    day_index = floor(raw_time / 24) + 1,
    
    # Calculate Time of Day (0-24h):
    time_hours = raw_time %% 24
  ) 

# ==========================================
# 2.1 Normalize Day Index
# ==========================================
# If the dataset starts on Day 5, shift it back to Day 1.
min_day <- min(actigram_data$day_index, na.rm = TRUE)

if (min_day > 1) {
  actigram_data$day_index <- actigram_data$day_index - (min_day - 1)
}

# Create the "Left" panel (Day N, 0-24 hours)
left_panel <- actigram_data %>%
  mutate(plot_x = time_hours,
         plot_y = day_index)

# Create the "Right" panel (Day N+1, 24-48 hours)
right_panel <- actigram_data %>%
  mutate(plot_x = time_hours + 24,
         plot_y = day_index - 1) %>%
  filter(plot_y >= 1)

# Combine them into one plotting dataset
plot_df <- bind_rows(left_panel, right_panel)

# ==========================================
# 3. Plotting with ggplot2
# ==========================================

ggplot(plot_df, aes(x = plot_x, y = plot_y)) +
  geom_rect(aes(
    xmin = plot_x, 
    xmax = plot_x + 0.25, # Adjust based on data frequency (e.g., 0.25 for 15 mins)
    
    # --- UPDATED LOGIC HERE ---
    # We use 'activity_adjusted' instead of 'activity'.
    # This means the bars only represent energy EXCEEDING the average.
    ymin = plot_y - (activity_adjusted / max(activity_adjusted, na.rm = TRUE)) * 1, 
    ymax = plot_y 
  ), fill = "black") +
  
  scale_y_reverse(
    breaks = unique(plot_df$plot_y),
    labels = paste("Day", unique(plot_df$plot_y))
  ) +
  scale_x_continuous(
    breaks = seq(0, 48, by = 6),
    labels = c("00:00", "06:00", "12:00", "18:00", "00:00", "06:00", "12:00", "18:00", "00:00"),
    limits = c(0, 48)
  ) +
  
  theme_bw() +
  labs(
    title = "Double-Plotted Actigram (Baseline Corrected)",
    subtitle = paste("Showing 48-hour window. Baseline Energy threshold:", round(avg_baseline, 2)),
    x = "Time of Day (Hours)",
    y = "Relative Day"
  ) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(color = "gray80") 
  ) +
  geom_vline(xintercept = 24, linetype = "dashed", color = "red", alpha = 0.5)
```



##** Actigram
```{r}

# ==========================================
# 1. Load and Filter Data
# ==========================================
# Assuming 'CorsanoAnalysismulti' is loaded in your R environment
df <- CorsanoAnalysismulti %>%
  filter(Subject == Subject3)

# DATA CHECK:
if("Steps" %in% names(df)) {
  df <- rename(df, activity = Steps)
} else {
  stop("Column 'Steps' not found. Please ensure the dataframe has a 'Steps' column.")
}

# ==========================================
# 2. Data Processing for Double Plotting
# ==========================================
# Logic Update:
# The 'Time' column is cumulative (e.g., 27.0 = 3 AM on Day 2).
# We need to extract the 0-24h time and the Day Index mathematically.

actigram_data <- df %>%
  mutate(
    # Ensure Time is numeric
    raw_time = as.numeric(Time),
    
    # Calculate Day Index: 
    # Time 0-24 is Day 1, 24-48 is Day 2, etc.
    # floor(raw_time / 24) gives 0 for Day 1, 1 for Day 2. We add 1 to make it 1-based.
    day_index = floor(raw_time / 24) + 1,
    
    # Calculate Time of Day (0-24h):
    # Use modulo operator %% to get the remainder after dividing by 24.
    time_hours = raw_time %% 24
  ) 

# ==========================================
# 2.1 Normalize Day Index
# ==========================================
# If the dataset starts on Day 5 (e.g., hours start > 96), this shifts it back to start at Day 1.
min_day <- min(actigram_data$day_index, na.rm = TRUE)

if (min_day > 1) {
  # Subtract (X - 1) from all values so the sequence starts at 1
  actigram_data$day_index <- actigram_data$day_index - (min_day - 1)
}

# Create the "Left" panel (Day N, 0-24 hours)
left_panel <- actigram_data %>%
  mutate(plot_x = time_hours,
         plot_y = day_index)

# Create the "Right" panel (Day N+1, 24-48 hours)
# We shift the time by +24, and shift the 'day association' back by 1.
# This means data from Day 2 (Day Index 2) will appear on Day 1's row (Plot Y 1), but at hours 24-48.
right_panel <- actigram_data %>%
  mutate(plot_x = time_hours + 24,
         plot_y = day_index - 1) %>%
  filter(plot_y >= 1)

# Combine them into one plotting dataset
plot_df <- bind_rows(left_panel, right_panel)

# ==========================================
# 3. Plotting with ggplot2
# ==========================================

ggplot(plot_df, aes(x = plot_x, y = plot_y)) +
  geom_rect(aes(
    xmin = plot_x, 
    xmax = plot_x + 0.25, # Width of ~15 min interval. Adjust if your data frequency differs.
    # To make bars go "UP" visually on a reversed Y-axis, we must SUBTRACT height from the baseline
    ymin = plot_y - (activity / max(activity, na.rm = TRUE)) * 1.5, 
    ymax = plot_y 
  ), fill = "black") +
  
  scale_y_reverse(
    breaks = unique(plot_df$plot_y),
    labels = paste("Day", unique(plot_df$plot_y))
  ) +
  scale_x_continuous(
    breaks = seq(0, 48, by = 6),
    labels = c("00:00", "06:00", "12:00", "18:00", "00:00", "06:00", "12:00", "18:00", "00:00"),
    limits = c(0, 48)
  ) +
  
  theme_bw() +
  labs(
    title = "Double-Plotted Actigram",
    subtitle = "Showing 48-hour window per row (Time cumulative)",
    x = "Time of Day (Hours)",
    y = "Relative Day"
  ) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(color = "gray80") 
  ) +
  geom_vline(xintercept = 24, linetype = "dashed", color = "red", alpha = 0.5)

```



#** Actigram with overlay
```{r}
# ==========================================
# 1. Load and Filter Data
# ==========================================
df <- CorsanoAnalysismulti %>%
  filter(Subject == "BWFD6Z76")

# DATA CHECK: Steps
if("Steps" %in% names(df)) {
  df <- rename(df, activity = Steps)
} else {
  stop("Column 'Steps' not found.")
}

# DATA CHECK: CBT (Red)
if("CBT" %in% names(df)) {
  df <- rename(df, temp = CBT)
} else {
  warning("Column 'CBT' not found. Creating empty column.")
  df$temp <- NA
}

# DATA CHECK: HR (Blue)
if("HR" %in% names(df)) {
  df <- rename(df, hr = HR)
  # Treat 0 as missing data so the line breaks instead of dipping
  df$hr[df$hr == 0] <- NA
} else {
  warning("Column 'HR' not found. Creating empty column.")
  df$hr <- NA
}

# DATA CHECK: HRV (Green)
if("HRV" %in% names(df)) {
  df <- rename(df, hrv = HRV)
} else {
  warning("Column 'HRV' not found. Creating empty column.")
  df$hrv <- NA
}

# DATA CHECK: Breath (Purple)
if("Breath" %in% names(df)) {
  df <- rename(df, breath = Breath)
} else {
  warning("Column 'Breath' not found. Creating empty column.")
  df$breath <- NA
}

# ==========================================
# 2. Data Processing for Double Plotting
# ==========================================

actigram_data <- df %>%
  mutate(
    raw_time = as.numeric(Time),
    day_index = floor(raw_time / 24) + 1,
    time_hours = raw_time %% 24
  ) 

# ==========================================
# 2.1 Normalize Day Index
# ==========================================
min_day <- min(actigram_data$day_index, na.rm = TRUE)
if (min_day > 1) {
  actigram_data$day_index <- actigram_data$day_index - (min_day - 1)
}

# ==========================================
# 2.2 Calculate Scaling Factors
# ==========================================
# We need global min/max to normalize the data to fit inside the rows (0-1 height)
max_act <- max(actigram_data$activity, na.rm = TRUE)

# CBT Scaling
min_temp <- min(actigram_data$temp, na.rm = TRUE)
max_temp <- max(actigram_data$temp, na.rm = TRUE)
temp_range <- max_temp - min_temp
if (is.na(temp_range) || temp_range == 0) temp_range <- 1 

# HR Scaling
#min_hr <- min(actigram_data$hr, na.rm = TRUE)
min_hr <- 50
max_hr <- max(actigram_data$hr, na.rm = TRUE)
hr_range <- max_hr - min_hr
if (is.na(hr_range) || hr_range == 0) hr_range <- 1 

# HRV Scaling
min_hrv <- min(actigram_data$hrv, na.rm = TRUE)
max_hrv <- max(actigram_data$hrv, na.rm = TRUE)
hrv_range <- max_hrv - min_hrv
if (is.na(hrv_range) || hrv_range == 0) hrv_range <- 1 

# Breath Scaling
min_breath <- min(actigram_data$breath, na.rm = TRUE)
max_breath <- max(actigram_data$breath, na.rm = TRUE)
breath_range <- max_breath - min_breath
if (is.na(breath_range) || breath_range == 0) breath_range <- 1 

# ==========================================
# 2.3 Create Panels
# ==========================================

# Create the "Left" panel (Day N, 0-24 hours)
left_panel <- actigram_data %>%
  mutate(plot_x = time_hours,
         plot_y = day_index)

# Create the "Right" panel (Day N+1, 24-48 hours)
# Shift time by +24, shift day index back by 1
right_panel <- actigram_data %>%
  mutate(plot_x = time_hours + 24,
         plot_y = day_index - 1) %>%
  filter(plot_y >= 1)

# Combine
plot_df <- bind_rows(left_panel, right_panel)

# ==========================================
# 3. Plotting with ggplot2
# ==========================================

ggplot(plot_df, aes(x = plot_x, y = plot_y)) +
  # 1. Activity Bars (Black)
  geom_rect(aes(
    xmin = plot_x, 
    xmax = plot_x + 0.25, 
    ymin = plot_y - (activity / max_act) * 0.9, 
    ymax = plot_y 
  ), fill = "black") + # Added alpha to bars to make lines more visible
  
  # 2. CBT Line (Red)
  geom_line(aes(
    group = plot_y,
    y = plot_y - ((temp - min_temp) / temp_range) * 0.9
  ), color = "red", size = 0.6, alpha = 0.8) +

  # 3. HR Line (Blue)
  geom_line(aes(
    group = plot_y,
    y = plot_y - ((hr - min_hr) / hr_range) * 1.25
  ), color = "blue", size = 0.6, alpha = 0.8) +

  # 4. HRV Line (Green)
#  geom_line(aes(
#    group = plot_y,
#    y = plot_y - ((hrv - min_hrv) / hrv_range) * 0.9
#  ), color = "green", size = 0.6, alpha = 0.8) +

  # 5. Breath Line (Purple)
#  geom_line(aes(
#    group = plot_y,
#    y = plot_y - ((breath - min_breath) / breath_range) * 0.9
#  ), color = "purple", size = 0.6, alpha = 0.8) +
  
  scale_y_reverse(
    breaks = unique(plot_df$plot_y),
    labels = paste("Day", unique(plot_df$plot_y))
  ) +
  scale_x_continuous(
    breaks = seq(0, 48, by = 6),
    labels = c("00:00", "06:00", "12:00", "18:00", "00:00", "06:00", "12:00", "18:00", "00:00"),
    limits = c(0, 48)
  ) +
  
  theme_bw() +
  labs(
    title = "Double-Plotted Actigram with Overlays",
    #subtitle = "Bars=Steps | Red=CBT | Blue=HR | Green=HRV | Purple=Breath (All Normalized)",
    subtitle = "Bars=Steps | Red=CBT | Blue=HR (All Normalized)",
    x = "Time of Day (Hours)",
    y = "Relative Day"
  ) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(color = "gray80") 
  ) +
  geom_vline(xintercept = 24, linetype = "dashed", color = "black", alpha = 0.3)
```









##** Actigram cbt
```{r}

# ==========================================
# 1. Load and Filter Data
# ==========================================
# Assuming 'CorsanoAnalysismulti' is loaded in your R environment
df <- CorsanoAnalysismulti %>%
  filter(Subject == "BWFD6Z76")

# DATA CHECK:
if("CBT" %in% names(df)) {
  df <- rename(df, activity = CBT)
} else {
  stop("Column 'CBT' not found. Please ensure the dataframe has the correct column.")
}

# ==========================================
# NEW STEP: Set Minimum CBT to Zero
# ==========================================
# Calculate the minimum value in the dataset (ignoring NAs)
cbt_min <- min(df$activity, na.rm = TRUE)

# Subtract the minimum from the activity column
# Now, the lowest temperature in the dataset will be 0
df$activity <- df$activity - cbt_min

# ==========================================
# 2. Data Processing for Double Plotting
# ==========================================
# Logic Update:
# The 'Time' column is cumulative (e.g., 27.0 = 3 AM on Day 2).
# We need to extract the 0-24h time and the Day Index mathematically.

actigram_data <- df %>%
  mutate(
    # Ensure Time is numeric
    raw_time = as.numeric(Time),
    
    # Calculate Day Index: 
    # Time 0-24 is Day 1, 24-48 is Day 2, etc.
    # floor(raw_time / 24) gives 0 for Day 1, 1 for Day 2. We add 1 to make it 1-based.
    day_index = floor(raw_time / 24) + 1,
    
    # Calculate Time of Day (0-24h):
    # Use modulo operator %% to get the remainder after dividing by 24.
    time_hours = raw_time %% 24
  ) 

# ==========================================
# 2.1 Normalize Day Index
# ==========================================
# If the dataset starts on Day 5 (e.g., hours start > 96), this shifts it back to start at Day 1.
min_day <- min(actigram_data$day_index, na.rm = TRUE)

if (min_day > 1) {
  # Subtract (X - 1) from all values so the sequence starts at 1
  actigram_data$day_index <- actigram_data$day_index - (min_day - 1)
}

# Create the "Left" panel (Day N, 0-24 hours)
left_panel <- actigram_data %>%
  mutate(plot_x = time_hours,
         plot_y = day_index)

# Create the "Right" panel (Day N+1, 24-48 hours)
# We shift the time by +24, and shift the 'day association' back by 1.
# This means data from Day 2 (Day Index 2) will appear on Day 1's row (Plot Y 1), but at hours 24-48.
right_panel <- actigram_data %>%
  mutate(plot_x = time_hours + 24,
         plot_y = day_index - 1) %>%
  filter(plot_y >= 1)

# Combine them into one plotting dataset
plot_df <- bind_rows(left_panel, right_panel)

# ==========================================
# 3. Plotting with ggplot2
# ==========================================

ggplot(plot_df, aes(x = plot_x, y = plot_y)) +
  geom_rect(aes(
    xmin = plot_x, 
    xmax = plot_x + 0.25, # Width of ~15 min interval. Adjust if your data frequency differs.
    # To make bars go "UP" visually on a reversed Y-axis, we must SUBTRACT height from the baseline.
    # Since we zeroed the min, 'activity' is now the delta from the lowest temp.
    # We normalize by the NEW max (which is the Range of the original data).
    ymin = plot_y - (activity / max(activity, na.rm = TRUE)) * 0.9, 
    ymax = plot_y 
  ), fill = "black") +
  
  scale_y_reverse(
    breaks = unique(plot_df$plot_y),
    labels = paste("Day", unique(plot_df$plot_y))
  ) +
  scale_x_continuous(
    breaks = seq(0, 48, by = 6),
    labels = c("00:00", "06:00", "12:00", "18:00", "00:00", "06:00", "12:00", "18:00", "00:00"),
    limits = c(0, 48)
  ) +
  
  theme_bw() +
  labs(
    title = "Double-Plotted Actigram (CBT Normalized)",
    subtitle = "Zero baseline = Minimum recorded CBT",
    x = "Time of Day (Hours)",
    y = "Relative Day"
  ) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line(color = "gray80") 
  ) +
  geom_vline(xintercept = 24, linetype = "dashed", color = "red", alpha = 0.5)

```







#** Chronotype **
```{r}




```




